---
title             : "US-China differences in cognition and perception across 12 tasks: Replicability, robustness, and within-culture variation"
shorttitle        : "US-China differences"
author:  
  - name          : "Anjie Cao*"
    affiliation   : "1"
    corresponding : yes    
    address       : "450 Jane Stanford Way, Stanford, 94305"
    email         : "anjiecao@stanford.edu" 
  - name          : "Alexandra Carstensen*"
    affiliation   : "2"
    email         : "abc@ucsd.edu"
  - name          : "Shan Gao"
    affiliation   : "3"
    email         : "FIXME"
  - name          : "Michael C. Frank"
    affiliation   : "1"
    address       : "450 Jane Stanford Way, Stanford, 94305"
    email         : "mcfrank@stanford.edu" 

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Department of Psychology, University of California, San Diego"
  - id            : "3"
    institution   : "Department of Psychology, University of Chicago"
  
  

authornote: |
  We gratefully acknowledge Alvin Tan, Joseph Outa, and the members of the Language and Cognition Lab at Stanford for comments and assistance. We are grateful for feedback and suggestions from Jenny Yang, Catherine Thomas, Ellen Reinhart, Erik Santoro, Kengthsagn Louis, Leslie Remache, Hazel Markus, and Shinobu Kitayama. We also want to thank the authors who provided the original experiment materials. Experiment 1 was previously reported in abbreviated form in the Proceedings of the Cognitive Science Society as Carstensen et al. (2020).
  
abstract: |

  Cultural differences between the US and China have been investigated using a broad array of psychological tasks measuring differences between cognition, language, perception, and reasoning. We examine the robustness of several classic experimental paradigms in cross-cultural psychology. Using online convenience samples of adults, we conducted two large-scale replications of 12 tasks previously reported to show cross-cultural differences. Our results showed a heterogeneous pattern of successes and failures: five tasks yielded robust cultural differences across both experiments, while six showed no difference between cultures, and one showed a small difference in the opposite direction. We observed moderate reliability in all of the multi-trial tasks, but there was little shared variation between tasks. Additionally, we did not see within-culture variation across a range of demographic factors in our samples. Finally, as in prior work, cross-cultural differences in cognition (in those tasks showing differences) were not strongly related to explicit measures of cultural identity and behavior. All of our tasks, data, and analyses are available openly online for reuse by future researchers, providing a foundation for future studies that seek to establish a robust and replicable science of cross-cultural difference.  


  
keywords          : "replication; cross-cultural differences; cognition; perception; US-China comparison"
wordcount         : "10486"
csl               : "apa6-meta.csl"
bibliography      : "library.bib"

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
#pdf_document
#papaja::apa6_pdf
latex_engine        : xelatex
header-includes   :
    - \usepackage{tabu}
    - \usepackage{adjustbox}
    - \usepackage{float}
    - \usepackage{graphicx}
    - \usepackage{longtable}
    - \usepackage{tabu}
    - \usepackage{setspace}% http://ctan.org/pkg/setspace
    - \AtBeginEnvironment{longtable}{\singlespacing}{\small}

appendix: 
  - "writing/sections/appendix_a.rmd"
  - "writing/sections/appendix_b.rmd"
  - "writing/sections/appendix_c.rmd"
  - "writing/sections/appendix_d.rmd"
---

```{r load_utility_packages, include = FALSE}
library(papaja)
library(rmarkdown)
library(tidyverse) 
library(here)
library(tidyboot)
library(glue)
library(cowplot)
library(kableExtra)
library(glue)
library(latex2exp)
library(ggcorrplot)
library(cowplot)
library(ggthemes)
library(pwr)
library(simr)
library(compute.es)

here::i_am("writing/CCRR_manuscript.Rmd")

r_refs("library.bib")
source(here("processing_pipelines/helper/plotting/plot_es.R"))
source(here("processing_pipelines/helper/plotting/plot_reliability.R"))
source(here("processing_pipelines/helper/plotting/plot_megaplot.R"))
source(here("processing_pipelines/helper/plotting/plot_table.R"))

```

```{r global_options, include = FALSE}

knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      cache = FALSE,
                      echo = FALSE
                      )
knitr::opts_chunk$set(dev = 'pdf')


knitr::opts_knit$set(root.dir = here())

theme_set(theme_classic(base_size = 11))
```

# Introduction

```{r child = "writing/sections/01_intro.Rmd"}
```

<!-- \end{landscape} -->

# Experiment 1

```{r child = "writing/sections/02_exp1_methods.Rmd"}
```

## Results

# ```{r child = "writing/sections/03_exp1_results.Rmd"}
# ```

## Discussion

```{r child = "writing/sections/04_exp1_discussion.Rmd"}
```

# Experiment 2

```{r child = "writing/sections/05_exp2_methods.Rmd"}
```

## Results

```{r child = "writing/sections/06_exp2_results.Rmd"}
```

## Discussion

```{r child = "writing/sections/07_exp2_discussion.Rmd"}

```

# Exploratory analyses

<!-- ## Mini meta-analysis -->

```{r child = "writing/sections/08_ea_mini_ma.Rmd"}
```

## Reliability assessment

```{r child = "writing/sections/09_ea_reliability_assessment.Rmd"}
```

## Relations between individual tasks

```{r child = "writing/sections/10_ea_relations_between_tasks.Rmd"}
```

## Demographic variation and explicit measures of cultural identity

```{r child = "writing/sections/11_demog_variation.Rmd"}
```

# General Discussion

```{r child = "writing/sections/12_general_discussion.Rmd"}
```

---
nocite: | 
---

```{r appendix}
#render_appendix("appendix.Rmd")
```

```{=tex}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
\newpage

# References

---
nocite: | 
   @na2020culture, @goddu2021toddlers
---

::: {#refs custom-style="Bibliography"}
:::

\newpage

\newpage

# (APPENDIX) Appendix {.unnumbered}

```{r child = "writing/sections/appendix_a.rmd"}
```

```{r child = "writing/sections/appendix_b.rmd"}
```

```{r child = "writing/sections/appendix_c.rmd"}
```

```{r child = "writing/sections/appendix_d.rmd"}
```

```{r child = "writing/sections/appendix_e.rmd"}
```


