---
title             : "Replicability of US-China differences in cognition and perception across 12 tasks"
shorttitle        : "Replicate US-China differences"
author:  
  - name          : "Anjie Cao*"
    affiliation   : "1"
    corresponding : yes    
    address       : "450 Jane Stanford Way, Stanford, 94305"
    email         : "anjiecao@stanford.edu" 
  - name          : "Alexandra Carstensen*"
    affiliation   : "2"
    email         : "abcarstensen@gmail.com"
  - name          : "Shan Gao"
    affiliation   : "3"
    email         : "FIXME"
  - name          : "Michael C. Frank"
    affiliation   : "1"
    address       : "450 Jane Stanford Way, Stanford, 94305"
    email         : "mcfrank@stanford.edu" 

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Department of Psychology, University of California, San Diego"
  - id            : "3"
    institution   : "FIXME"
  
  

authornote: |
  We gratefully acknowledge Alvin Tan, Joseph Outa, and the members of the Language and Cognition Lab at Stanford for comments and assistance. Experiment 1 was previously reported in abbreviated form in the Proceedings of the Cognitive Science Society as Carstensen et al. (2020).
  
abstract: |
    Cultural differences between the US and China have been investigated using a broad array of psychological tasks measuring differences between cognition, language, perception, and reasoning. We conducted two large-scale replications of a selection of 12 tasks previously reported to show cross-cultural differences, using online convenience samples of adults. Five of these tasks showed robust cross-cultural differences, while six showed no difference and one showed a small difference in the opposite direction. Tasks showing cross-cultural differences tended to have multiple trials measuring high-level reasoning and language; those that did not show cross-cultural difference included measures of attention/perception, implicit social processes, or were initially designed to show differences in children. As in prior work, cross-cultural differences in cognition (in those tasks showing differences) were not strongly related to explicit measures of cultural identity and behavior.

  
keywords          : "FIXME"
wordcount         : "FIXME"
csl               : "apa6-meta.csl"
bibliography      : "library.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
#pdf_document
#papaja::apa6_pdf
latex_engine        : xelatex
---

```{r setup, include = FALSE}
library("papaja")
r_refs("library.bib")
```

```{r load_utility_packages, include = FALSE}
library(papaja)
library(rmarkdown)
library(tidyverse) 
library(here)
library(glue)
```


```{r global_options, include = FALSE}
here::i_am("writing/CCRR_manuscript.Rmd")

knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      cache = FALSE,
                      echo = FALSE
                      )
knitr::opts_chunk$set(dev = 'pdf')


knitr::opts_knit$set(root.dir = here())

theme_set(theme_classic(base_size = 11))
```



# Introduction

```{r child = "writing/sections/01_intro.Rmd"}
```

# Experiment 1

In Experiment 1, our goal was to evaluate cross-cultural differences in a variety of constructs. We assembled a web-based battery of tasks and tested these on a snowball sample of US and Chinese participants. 

## Methods 


```{r child = "writing/sections/02_exp1_methods.Rmd"}
```

## Results

```{r child = "writing/sections/03_exp1_results.Rmd"}
```

## Discussion

```{r child = "writing/sections/04_exp1_discussion.Rmd"}
```

# Experiment 2

Experiment 2 was designed to follow up on Experiment 1 and further evaluate cross-cultural differences across a battery of tasks. Since several of our tasks in Experiment 1 yielded no evidence for cross-cultural differences, we replaced these with alternative tasks selected to address similar or related constructs. We replaced the Ebbinghaus Illusion with a measure of Change Detection that had been argued to index context sensitivity [@masuda2006culture]. We replaced the child-appropriate causal attribution task with a task designed for adults [@morris1994culture]. We also included two tasks measuring linguistic or semantic intuitions more broadly (Taxonomic/Thematic Similarity and Semantic Intuition), following up on the detection of cross-cultural differences in the Picture Free Description task. Although our goal in Experiment 2 was to evaluate a further set of tasks, we also included the RMTS, Picture Free Description, and Raven’s Progressive Matrices tasks to replicate our results from Experiment 1, and we included a modified version of Symbolic Self-Inflation to address several issues with the earlier version of the task. 

In Experiment 2, we made use of crowd-sourcing services – rather than snowball sampling – as our participant recruitment channel. We had two rationales. First, in Experiment 1 our samples were quite young (due to the use of email and social media to populations of university students for recruitment). A younger sample might be more exposed to international media and influences and be less likely to show distinct cross-cultural differences. Second, we were concerned that being recruited by friends and family (as in a snowball sample) might prime interdependent thinking among our participants, leading to decreased cross-cultural differences [@markus1992and]. 

## Methods

```{r child = "writing/sections/05_exp2_methods.Rmd"}
```

<!-- ```{r child = "sections/06_exp2_results.Rmd"} -->
<!-- ``` -->

<!-- ```{r child = "sections/07_exp2_discussion.Rmd"} -->
<!-- ``` -->


<!-- # Exploratory analysis  -->

<!-- ```{r child = "sections/08_exploratory_analysis.Rmd"} -->
<!-- ``` -->


<!-- # General Discussion -->
<!-- ```{r child = "sections/09_general_discussion.Rmd"} -->
<!-- ``` -->



---
nocite: | 
...
  
```{r appendix}
#render_appendix("appendix.Rmd")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
