---
title: "02_reliability_assessment"
author: "anjie"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(here)
library(splithalf)

d1 <- read_csv(here("data/03_processed_data/exp1/tidy_main.csv"))
d2 <- read_csv(here("data/03_processed_data/exp2/tidy_main.csv"))

source(here("processing_pipelines/helper/calculate_reliability.R"))
```


Here we only calculate splithalf reliability for tasks with multiple trials (>2 trial) and for trials that provide critical tests on cross cultural differences. Below is a breakdown on how the calculation is done: 

For study 1, this includes: 
- RMTS
- Free Description (FD)
- Ebbignhaus Illusion (EBB): only with trials in the illusional context. 
- Ravens (RV)

For study 2, this includes: 
- RMTS 
- Free Description (FD)
- Change Detection (CD): only with trials in which changes occur in the background 
- Causal Attribution (CA): only with items on the scale for situational attribution 
- Triads (TD)
- Ravens (RV)



```{r}

d1_reliability <- get_d1_reliability(d1, tasks = c("RMTS", "EBB", "FD", "RV")) %>% mutate(exp = "exp1")
d2_reliability <- get_d2_reliability(d2, tasks = c("RMTS", "FD", "CD", "CA", "TD","RV"))

reliability_df <- bind_rows(d1_reliability %>% mutate(exp = "exp1"),
                            d2_reliability %>% mutate(exp = "exp2")) %>% 
                  mutate(type = "all")
```

We also examine the by-culture reliability to make sure there is no consistent pattern across culture. We speculate some bigger difference between cultures may have something to do with one culture reaches ceiling effects. 



```{r}
d1_us_reliability <- get_d1_reliability(d1 %>% filter(culture == "US"), 
                                        tasks = c("RMTS", "EBB", "FD", "RV")) %>% 
                    mutate(exp = "exp1", 
                           culture = "US")
      
d1_cn_reliability <- get_d1_reliability(d1 %>% filter(culture == "CN"), 
                                        tasks = c("RMTS", "EBB", "FD", "RV")) %>% 
                    mutate(exp = "exp1", 
                           culture = "CN")


d2_us_reliability <- get_d2_reliability(d2 %>% filter(culture == "US"), 
                                     tasks = c("RMTS", "FD", "CD", "CA", "TD","RV")) %>% 
                  mutate(exp = "exp2", 
                           culture = "US")

d2_cn_reliability <- get_d2_reliability(d2 %>% filter(culture == "CN"), 
                                     tasks = c("RMTS", "FD", "CD", "CA", "TD","RV")) %>% 
                  mutate(exp = "exp2", 
                           culture = "CN")

by_culture_reliability <- bind_rows(d2_us_reliability, d2_cn_reliability, 
                                    d1_us_reliability, d1_cn_reliability) %>% 
                          mutate(type = "by_culture")
```


```{r}
main_reliability <- bind_rows(reliability_df, by_culture_reliability)
saveRDS(main_reliability, here("cached_results/ea/reliability.RDS"))
```


# plotting function preview: 



```{r}

main_reliability %>% 
  mutate(
    print_task_name = case_when(
     task_name == "TD" ~ "Triads", 
     task_name == "RV" ~ "Ravens", 
     task_name == "RMTS" ~ "RMTS", 
     task_name == "FD" ~ "Picture Free Description", 
     task_name == "EBB" ~ "Ebbinghaus Illusion",
     task_name == "CD" ~ "Change Detection", 
     task_name == "CA" ~ "Adult Causal Attribution"
    )
  ) %>% 
  filter(type == "all") %>% 
  ggplot(aes(x = print_task_name, 
             y = spearmanbrown, 
             ymin = SB_low, 
             ymax = SB_high,
             group = exp, 
             shape = exp
             )) + 
  ylab("Spearman-Brown Correlation") + 
  xlab("") + 
  geom_pointrange(position = position_dodge(width = 0.6)) + 
  guides(shape=guide_legend(title="Experiment")) + 
  ylim(0, 1) + 
  coord_flip() + 
  theme_classic()

```

