---
title: "03_relations_between_tasks.rmd"
author: "anjie"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

ˆ
```{r}
library(tidyverse)
library(here)
library(reshape2)
library(psych)
library(corrplot)
library(psych)
library(ggplot2)
library(car)

d1 <- read_csv(here("data/03_processed_data/exp1/tidy_main.csv"))
d2 <- read_csv(here("data/03_processed_data/exp2/tidy_main.csv"))

```

Now after establishing the reliability of multi-trial tasks, we would like to consider the correlations. Below are the tasks that we are going to consider

For study 1, this includes: 

- RMTS
- Free Description (FD)
- Ebbignhaus Illusion (EBB): only with trials in the illusional context. 
- Ravens (RV)



For study 2, this includes: 

- RMTS 
- Free Description (FD)
- Change Detection (CD): only with trials in which changes occur in the background 
- Causal Attribution (CA): only with items on the scale for situational attribution 
- Triads (TD)
- Ravens (RV)


# study 1

```{r}

clean_d1_ssi <- d1 %>% 
  filter(task_name == "SI") %>% 
  filter(resp_type == "inflation_score_ratio") %>% 
  mutate(resp_num = as.numeric(resp)) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_ebb <- d1 %>% 
  filter(task_name == "EBB", task_info == "IL") %>% 
  group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp))

clean_d1_rmts <- d1 %>% 
  filter(task_name == "RMTS") %>% 
   group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp))

clean_d1_hz <- d1 %>% 
  filter(task_name == "HZ", resp_type == "hz_height") %>% 
  mutate(resp_num = resp) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_up <- d1 %>% 
  filter(task_name == "CP") %>% 
  mutate(resp_num = resp) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_rv <- d1 %>% 
  filter(task_name == "RV") %>% 
   group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp)) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_fd <- d1 %>% 
  filter(task_name == "FD", resp_type == "first_mention_focal") %>% 
   group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp)) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_ca <- d1 %>% 
  filter(task_name == "CA", resp_type == "situation_attribution")%>% 
  group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp)) %>% 
  select(subject, culture, task_name, resp_num)


d1_task_summary <- bind_rows(clean_d1_ca, 
          clean_d1_ebb, 
          clean_d1_fd, 
          clean_d1_hz, 
          clean_d1_rmts, 
          clean_d1_rv, 
          clean_d1_ssi, 
          clean_d1_up) %>% 
  pivot_wider(names_from = task_name, 
              values_from = resp_num) %>% 
  select(-subject)

d1_corr_mat <- cor(d2_task_summary)
melted_d1_corr_mat <- melt(d1_corr_mat)
melted_d1_corr_mat %>% 
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() 

corrplot(d1_corr_mat, method = "number")

```
## imputed with mean value 

```{r}
d1_mean <- d1_task_summary %>% 
  pivot_longer(cols = -c(subject, culture), 
               names_to = "task", 
               values_to = "value") %>% 
  group_by(task) %>% 
  summarise(mean = mean(value, na.rm = TRUE))

imputed_d1_task_summary <- d1_task_summary %>% 
  mutate(
  CA = case_when(
    is.na(CA) ~ filter(d1_mean, task == "CA")$mean, 
    TRUE ~ CA
  ), 
  EBB = case_when(
    is.na(EBB) ~ filter(d1_mean, task == "EBB")$mean, 
    TRUE ~ EBB
  ),
  FD = case_when(
    is.na(FD) ~ filter(d1_mean, task == "FD")$mean, 
    TRUE ~ FD
  ),
  HZ = case_when(
    is.na(HZ) ~ filter(d1_mean, task == "HZ")$mean, 
    TRUE ~ HZ
  ),
  RMTS = case_when(
    is.na(RMTS) ~ filter(d1_mean, task == "RMTS")$mean, 
    TRUE ~ RMTS
  ),
  RV = case_when(
    is.na(RV) ~ filter(d1_mean, task == "RV")$mean, 
    TRUE ~ RV
  ),
  SI = case_when(
    is.na(SI) ~ filter(d1_mean, task == "SI")$mean, 
    TRUE ~ SI
  ),
  CP = case_when(
    is.na(CP) ~ filter(d1_mean, task == "CP")$mean, 
    TRUE ~ CP
  ),
  ) 

imputed_d1_corr_mat <- cor(imputed_d1_task_summary %>% ungroup() %>% select(-subject, -culture))
melted_imputed_d1_corr_mat <- melt(imputed_d1_corr_mat)
melted_imputed_d1_corr_mat %>% 
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() 

corrplot(imputed_d1_corr_mat, method = "number")
```

## deletion

```{r}
deletion_d1_task_summary <- drop_na(d1_task_summary)


deletion_d1_corr_mat <- cor(deletion_d1_task_summary %>% ungroup() %>% select(-subject, -culture))
melted_deletion_d1_corr_mat <- melt(deletion_d1_corr_mat)
melted_deletion_d1_corr_mat %>% 
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() 

corrplot(deletion_d1_corr_mat, method = "number")
```



For study 2, this includes: 
- RMTS 
- Free Description (FD)
- Change Detection (CD): only with trials in which changes occur in the background 
- Causal Attribution (CA): only with items on the scale for situational attribution 
- Triads (TD)
- Ravens (RV)


# study 2

since we are dealing with missing data, two approaches were considered

## imputed with mean value

```{r}


clean_d2_CD <- d2 %>% 
  filter(task_name == "CD", task_info == "context") %>% 
  group_by(subject, culture, task_name) %>% 
  filter(!resp == "null") %>% 
  summarise(resp_num = mean(as.numeric(resp)))

clean_d2_SSI <- d2 %>% 
  filter(task_name == "SSI", resp_type == "task_score_ratio") %>%
  mutate(resp_num = as.numeric(resp))

clean_d2_CA <- d2 %>% 
  filter(task_name == "CA", task_info == "situational") %>% 
  group_by(subject, culture, task_name) %>% 
  filter(!is.na(resp)) %>% 
  summarise(resp_num = mean(as.numeric(resp)))

clean_d2_TD <- d2 %>% 
  filter(task_name == "TD", task_info == "triads") %>% 
  group_by(subject, culture, task_name) %>% 
  filter(!is.na(resp)) %>% 
  summarise(resp_num = mean(as.numeric(as.logical(resp))))

clean_d2_SeI <- d2 %>% 
  filter(task_name == "SeI", task_info == "critical") %>% 
  mutate(resp = case_when(
    resp == "causal_historical" ~ 1, 
    TRUE ~ 0)) %>% 
  group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(as.numeric(resp)))


d2_task_summary <- d2 %>% 
  filter(task_name %in% c("RMTS","RV","FD"))  %>% 
  mutate(resp_num = as.numeric(resp))  %>% 
  group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp_num)) %>%
  bind_rows(clean_d2_CD, clean_d2_SSI, clean_d2_CA, 
            clean_d2_TD, clean_d2_SeI)  %>% 
  select(subject, culture, task_name, resp_num) %>% 
  ungroup() %>% 
  pivot_wider(names_from = task_name, 
              values_from = resp_num) %>% 
  select(-subject, -culture)


# have many missing data

#imputation mean 
d2_task_mean <- d2_task_summary %>% 
  pivot_longer(cols = everything(), 
               names_to = "task", 
               values_to = "value") %>% 
  group_by(task) %>% 
  summarise(mean = mean(value, na.rm = TRUE))

imputed_d2_task_summary <- d2_task_summary %>% 
  mutate(
  CD = case_when(
    is.na(CD) ~ filter(d2_task_mean, task == "CD")$mean, 
    TRUE ~ CD
  ), 
  RMTS = case_when(
    is.na(RMTS) ~ filter(d2_task_mean, task == "RMTS")$mean, 
    TRUE ~ RMTS
  ),
  RV = case_when(
    is.na(RV) ~ filter(d2_task_mean, task == "RV")$mean, 
    TRUE ~ RV
  ),
  TD = case_when(
    is.na(TD) ~ filter(d2_task_mean, task == "TD")$mean, 
    TRUE ~ TD
  ),
  CA = case_when(
    is.na(CA) ~ filter(d2_task_mean, task == "CA")$mean, 
    TRUE ~ CA
  ),
  FD = case_when(
    is.na(FD) ~ filter(d2_task_mean, task == "FD")$mean, 
    TRUE ~ FD
  ),
  SeI = case_when(
    is.na(SeI) ~ filter(d2_task_mean, task == "SeI")$mean, 
    TRUE ~ SeI
  ),
  SSI = case_when(
    is.na(SSI) ~ filter(d2_task_mean, task == "SSI")$mean, 
    TRUE ~ SSI
  )
  ) 


d2_corr_mat <- cor(imputed_d2_task_summary)
corrplot(d2_corr_mat, method = "number")
melted_d2_corr_mat <- melt(d2_corr_mat)
melted_d2_corr_mat %>% 
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() 




```

## deletion

```{r}

# or do deletion
deletion_d2_task_summary <- drop_na(d2_task_summary)

d2_corr_mat <- cor(deletion_d2_task_summary)
corrplot(d2_corr_mat, method = "number")
melted_d2_corr_mat <- melt(d2_corr_mat)
melted_d2_corr_mat %>% 
  ggplot(aes(x = Var1, y = Var2, fill = value)) + 
  geom_tile() 
```
# cached the correlation matrices 

```{r}
cor_summary_df <- bind_rows(
  d1_task_summary %>% mutate(study = "study_1") %>% ungroup() %>% select(-subject, -culture),
  d2_task_summary %>% mutate(study = "study_2")
)

melted_d1_corr_mat_imputed <- melt(cor(imputed_d1_task_summary %>% ungroup() %>% select(-subject, -culture))) %>% mutate(study = "study_1") %>% mutate(missing_data = "imputed")
melted_d1_corr_mat_deletion <- melt(cor(deletion_d1_task_summary %>% ungroup() %>% select(-subject, -culture))) %>% mutate(study = "study_1") %>% mutate(missing_data = "deleted")
melted_d2_corr_mat_imputed <- melt(cor(imputed_d2_task_summary)) %>% mutate(study = "study_2") %>% 
  mutate(missing_data = "imputed")
melted_d2_corr_mat_deletion <- melt(cor(deletion_d2_task_summary)) %>% mutate(study = "study_2") %>% 
  mutate(missing_data = "deleted")

cor_main_df <- bind_rows(melted_d1_corr_mat_imputed,
                         melted_d1_corr_mat_deletion,
                         melted_d2_corr_mat_imputed, melted_d2_corr_mat_deletion) %>% 
  rename(task_1 = Var1, task_2 = Var2)

saveRDS(cor_summary_df, here("cached_results/ea/cor_summary_df.RDS"))
saveRDS(cor_main_df, here("cached_results/ea/cor_main_df.RDS"))
```



# factor analysis 

## check factorability of the data 

Bartlett’s Test of Sphericity
Small values of the significance level indicate a factor analysis maybe useful
but apparently it's not the case
```{r}
cortest.bartlett(d1_task_summary %>% ungroup() %>% select(-subject, -culture))
cortest.bartlett(d2_task_summary)

```

## scree plots

### Study 1

```{r}
fafitfree <- fa(d1_task_summary %>% ungroup() %>% select(-subject, -culture), nfactors = ncol(d1_task_summary %>% ungroup() %>% select(-subject, -culture)), rotate = "none")
n_factors <- length(fafitfree$e.values)
scree     <- data.frame(
  Factor_n =  as.factor(1:n_factors), 
  Eigenvalue = fafitfree$e.values)
ggplot(scree, aes(x = Factor_n, y = Eigenvalue, group = 1)) + 
  geom_point() + geom_line() +
  xlab("Number of factors") +
  ylab("Initial eigenvalue") +
  labs( title = "Scree Plot for Study 1", 
        subtitle = "(Based on the unreduced correlation matrix)")
```

### Study 2

```{r}
fafitfree <- fa(d2_task_summary, nfactors = ncol(d2_task_summary), rotate = "none")
n_factors <- length(fafitfree$e.values)
scree     <- data.frame(
  Factor_n =  as.factor(1:n_factors), 
  Eigenvalue = fafitfree$e.values)
ggplot(scree, aes(x = Factor_n, y = Eigenvalue, group = 1)) + 
  geom_point() + geom_line() +
  xlab("Number of factors") +
  ylab("Initial eigenvalue") +
  labs( title = "Scree Plot for study 2", 
        subtitle = "(Based on the unreduced correlation matrix)")
```


