---
title: "04_demographics_variation"
author: "anjie"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(here)


d1 <- read_csv(here("data/03_processed_data/exp1/tidy_main.csv"))
d2 <- read_csv(here("data/03_processed_data/exp2/tidy_main.csv"))
d2_demog <- read_csv(here("data/03_processed_data/exp2/tidy_demog.csv"))


```

# task scale relationship 

study 2 only 

```{r}
# reverse scoring local 
# higher score = global 
# lower score = global 
demog_d_scale <- d2_demog %>% 
  mutate(scale_type = case_when(
    grepl("identity_local", demog_question) ~ "identity_local",
    grepl("identity_global", demog_question) ~ "identity_global",
    grepl("consumption_local", demog_question) ~ "consumption_local",
    grepl("consumption_global", demog_question) ~ "consumption_global",
    grepl("cosmopolitanism", demog_question) ~ "cosmopolitanism", 
    TRUE ~ "non_scale"
  )) %>% 
  filter(!(scale_type == "non_scale")) %>% 
  mutate(demog_response = as.numeric(demog_response) + 1) %>% 
  mutate(demog_response = case_when(
    grepl("identity_local", demog_question) ~ -demog_response, 
    grepl("consumption_local", demog_question) ~ -demog_response,
    TRUE ~ demog_response
  )) %>% 
  group_by(subject, culture) %>% 
  summarise(scale_sum_score = sum(demog_response))

d2_with_scale <- d2 %>% 
    left_join(demog_d_scale, by = c("subject", "culture")) 

```


## RMTS 

### figure 

```{r}
d2_with_scale %>% 
  filter(task_name == "RMTS") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(relational_match = mean(as.numeric(resp))) %>% 
  ggplot(aes(x = scale_sum_score,  
             y = relational_match, 
             color = culture)) + 
  geom_jitter(alpha = .3) + 
  geom_smooth(method = "lm") + 
  labs(title = "rmts with scale")
```
### model - needs controlling for the demographic effect 

```{r}
rmts_d <- d2_with_scale %>% 
  filter(task_name == "RMTS") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(relational_match = mean(as.numeric(resp)))

rmts_scale_m <- lm(relational_match ~ scale_sum_score, data = rmts_d)
summary(rmts_scale_m)
```


## Free Description (FD)

### figure 

```{r}
d2_with_scale %>% 
  filter(task_name == "FD") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(first_mention_rate = mean(as.numeric(resp))) %>% 
  ggplot(aes(x = scale_sum_score,  
             y = first_mention_rate, 
             color = culture)) + 
  geom_jitter(alpha = .3) + 
  geom_smooth(method = "lm") + 
  labs(title = "Free description with scale")
```

### model 


```{r}
fd_d <- d2_with_scale %>% 
  filter(task_name == "FD") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(first_mention_rate = mean(as.numeric(resp)))

rmts_scale_m <- lm(first_mention_rate ~ scale_sum_score, data = fd_d)
summary(rmts_scale_m)
```


## Change Detection (CD): only with trials in which changes occur in the background 

### figure 


```{r}
d2_with_scale %>% 
  filter(task_name == "CD", task_info == "context") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  filter(resp != "null") %>% 
  summarise(rt_at_context_condition = mean(as.numeric(resp)), na.rm = TRUE) %>% 
  ggplot(aes(x = scale_sum_score,  
             y = log(rt_at_context_condition), 
             color = culture)) + 
  geom_jitter(alpha = .3) + 
  geom_smooth(method = "lm") + 
  labs(title = "RT at context condition with scale")
```

### model 

```{r}
cd_d <- d2_with_scale %>% 
  filter(task_name == "CD", task_info == "context") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  filter(resp != "null") %>% 
  summarise(rt_at_context_condition = mean(as.numeric(resp)), na.rm = TRUE) 

cd_scale_m <- lm(log(rt_at_context_condition) ~ scale_sum_score, data = cd_d)
summary(cd_scale_m)
```

## Causal Attribution 

### figure

```{r}
d2_with_scale %>% 
  filter(task_name == "CA", task_info == "situational") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(rating_at_situational = mean(as.numeric(resp)), na.rm = TRUE) %>% 
  ggplot(aes(x = scale_sum_score,  
             y = rating_at_situational, 
             color = culture)) + 
  geom_jitter(alpha = .3) + 
  geom_smooth(method = "lm") + 
  labs(title = "Rating at situational condition with scale")
```

### model 

```{r}
ca_d <- d2_with_scale %>% 
  filter(task_name == "CA", task_info == "situational") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(rating_at_situational = mean(as.numeric(resp), na.rm = TRUE)) 

ca_scale_m <- lm(rating_at_situational ~ scale_sum_score, data = ca_d)
summary(ca_scale_m)
```

## Triads 

### figure 
```{r}
d2_with_scale %>% 
  filter(task_name == "TD", task_info == "triads") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(proportion_tax_match = mean(as.numeric(as.logical(resp))), na.rm = TRUE) %>% 
  ggplot(aes(x = scale_sum_score,  
             y = proportion_tax_match, 
             color = culture)) + 
  geom_jitter(alpha = .3) + 
  geom_smooth(method = "lm") + 
  labs(title = "Proportion tax match with scale")
```

### model - needs controls

```{r}
td_d <- d2_with_scale %>% 
  filter(task_name == "TD", task_info == "triads") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(proportion_tax_match = mean(as.numeric(as.logical(resp))), na.rm = TRUE) 

td_scale_m <- lm(proportion_tax_match ~ scale_sum_score, data = td_d)
summary(td_scale_m)
```

## Ravens

### figure 

```{r}
d2_with_scale %>% 
  filter(task_name == "RV") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(proportion_correct = mean(as.numeric(resp)), na.rm = TRUE) %>% 
  ggplot(aes(x = scale_sum_score,  
             y = proportion_correct, 
             color = culture)) + 
  geom_jitter(alpha = .3) + 
  geom_smooth(method = "lm") + 
  labs(title = "RV Proportion correct with scale")
```


### model 

```{r}
rv_d <- d2_with_scale %>% 
  filter(task_name == "RV") %>% 
  group_by(subject, culture, scale_sum_score) %>% 
  summarise(proportion_correct = mean(as.numeric(resp)), na.rm = TRUE) 

rv_scale_m <- lm(proportion_correct ~ scale_sum_score, data = rv_d)
summary(rv_scale_m)
```


# demographic realtionship (rice/wheat)

# within culure relationship 




