---
title: "04_demographics_variation"
author: "anjie"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r}
library(tidyverse)
library(here)
library(broom)


d1 <- read_csv(here("data/03_processed_data/exp1/tidy_main.csv"))
d2 <- read_csv(here("data/03_processed_data/exp2/tidy_main.csv"))

d1_demog <- read_csv(here("data/03_processed_data/exp1/tidy_demog.csv"))
d2_demog <- read_csv(here("data/03_processed_data/exp2/tidy_demog.csv"))

us_regions <- read_csv(here("data/03_processed_data/us_regions.csv"))
cn_regions <- read_csv(here("data/03_processed_data/cn_regions.csv"))

```



# Task-global identity relationships 




Since we only collected scales for study 2, here we are only running the test with study 2

```{r}
d2_with_scale <- d2 %>% 
  left_join(d2_demog %>% 
  mutate(scale_type = case_when(
    grepl("identity_local", demog_question) ~ "identity_local",
    grepl("identity_global", demog_question) ~ "identity_global",
    grepl("consumption_local", demog_question) ~ "consumption_local",
    grepl("consumption_global", demog_question) ~ "consumption_global",
    grepl("cosmopolitanism", demog_question) ~ "cosmopolitanism", 
    TRUE ~ "non_scale"
  )) %>% 
  filter(!(scale_type == "non_scale")) %>% 
  mutate(demog_response = as.numeric(demog_response) + 1, 
         demog_response = case_when(
           grepl("local", scale_type) ~ -demog_response, 
           TRUE ~ demog_response
         )) %>% 
  group_by(subject, culture) %>% 
  summarise(scale_sum_score = sum(demog_response)), 
  by = c("subject", "culture"))


```

```{r}

# RMTS, FD, CD, SSI, CA, TD, SeI, RV
# cleaning 
clean_d2_CD <- d2_with_scale %>% 
  filter(task_name == "CD", task_info == "context") %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  filter(!resp == "null") %>% 
  summarise(resp_num = mean(as.numeric(resp)))

clean_d2_SSI <- d2_with_scale %>% 
  filter(task_name == "SSI", resp_type == "task_score_ratio") %>%
  mutate(resp_num = as.numeric(resp))

clean_d2_CA <- d2_with_scale %>% 
  filter(task_name == "CA", task_info == "situational") %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  filter(!is.na(resp)) %>% 
  summarise(resp_num = mean(as.numeric(resp)))

clean_d2_TD <- d2_with_scale %>% 
  filter(task_name == "TD", task_info == "triads") %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  filter(!is.na(resp)) %>% 
  summarise(resp_num = mean(as.numeric(as.logical(resp))))

clean_d2_SeI <- d2_with_scale %>% 
  filter(task_name == "SeI", task_info == "critical") %>% 
  mutate(resp = case_when(
    resp == "causal_historical" ~ 1, 
    TRUE ~ 0)) %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  summarise(resp_num = mean(as.numeric(resp)))


d2_task_giscale <- d2_with_scale  %>% 
  filter(task_name %in% c("RMTS","RV","FD"))  %>% 
  mutate(resp_num = as.numeric(resp))  %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  summarise(resp_num = mean(resp_num)) %>% 
  bind_rows(clean_d2_CD, clean_d2_SSI, clean_d2_CA, 
            clean_d2_TD, clean_d2_SeI) %>% 
  group_by(task_name) %>% 
  nest() |>
  mutate(mod = map(data, 
                   function (df) lm(resp_num ~ scale_sum_score * culture, 
                                    data = df)), 
         tidy = map(mod, tidy)) |>
  select(-mod, -data) |>
  unnest(cols = c(tidy)) |>
  filter(term %in% c("scale_sum_score","scale_sum_score:cultureUS")) 

d2_task_giscale$adjusted = p.adjust(d2_task_giscale$p.value, method = "bonferroni")

saveRDS(d2_task_giscale, here("cached_results/ea/task_giscale_df.RDS"))

d2_task_giscale|>
  knitr::kable(digits = 3)
```





# Regional differences 

```{r}

toneless_dict <- pinyin::pydic("toneless")
demog_province_cleaned <- 
  bind_rows(d1_demog %>% mutate(study = "d1"), 
            d2_demog %>% mutate(study = "d2")) %>% 
  filter(demog_question == "state_grewup") %>% 
  rowwise() %>% 
  mutate(demog_response_clean = case_when(
    culture == "CN" ~ as.character(pinyin::py(demog_response, toneless_dict, 
                                              sep = "",
                                       other_replace = NULL)), 
    TRUE ~ demog_response
  )) %>% 
  mutate(demog_response_clean = case_when(
  demog_response_clean == "hena" ~ "Henan",
  demog_response_clean == "jita" ~ "Others",
  demog_response_clean == "haina" ~ "Hainan",
  demog_response_clean == "huna" ~ "Hunan",
  demog_response_clean == "andong" ~ "Guangdong",
  demog_response_clean == "namenggu" ~ "Inner Mongolia",
  demog_response_clean == "jinghai" ~ "Qinghai",
  demog_response_clean == "angxi" ~ "Guangxi",
  demog_response_clean == "anxi" ~ "Guangxi",
  demog_response_clean == "yunna" ~ "Yunnan",
  demog_response == "山西" ~ "Shanxi",
  demog_response == "宁夏" ~ "Ningxia",
  demog_response == "陕西" ~ "Shaanxi",
  TRUE ~ demog_response_clean
)) %>% 
  mutate(demog_response_clean = tolower(demog_response_clean)) %>% 
  left_join(us_regions %>% 
              mutate(demog_response_clean = tolower(State)) %>% 
              select(Region, Coast, demog_response_clean), by = "demog_response_clean"
            ) %>% 
  left_join(cn_regions %>% 
              mutate(demog_response_clean = tolower(Province)) %>% 
              select(PercentPaddy, RiceCat, demog_response_clean), 
            by = "demog_response_clean") %>% 
    janitor::clean_names() %>% 
   mutate(rice_cat = case_when(rice_cat == 1 ~ "wheat", 
                              rice_cat == 2 ~ "rice"))




us_d1_region_d <- demog_province_cleaned %>% 
  filter(study == "d1", culture == "US") %>% 
  select(subject, study, culture, study, coast, region)

us_d2_region_d <- demog_province_cleaned %>% 
  filter(study == "d2", culture == "US") %>% 
  select(subject, study, culture, study, coast, region)

cn_d1_region_d <- demog_province_cleaned %>% 
  filter(study == "d1", culture == "CN") %>% 
  select(subject, study, culture, study, rice_cat)

cn_d2_region_d <- demog_province_cleaned %>% 
  filter(study == "d2", culture == "CN") %>% 
  select(subject, study, culture, study, rice_cat)
 
```

## study 1


```{r}
clean_d1_ssi <- d1 %>% 
  filter(task_name == "SI") %>% 
  filter(resp_type == "inflation_score_ratio") %>% 
  mutate(resp_num = as.numeric(resp)) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_ebb <- d1 %>% 
  filter(task_name == "EBB", task_info == "IL") %>% 
  group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp))

clean_d1_rmts <- d1 %>% 
  filter(task_name == "RMTS") %>% 
   group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp))

clean_d1_hz <- d1 %>% 
  filter(task_name == "HZ", resp_type == "hz_height") %>% 
  mutate(resp_num = resp) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_up <- d1 %>% 
  filter(task_name == "CP") %>% 
  mutate(resp_num = resp) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_rv <- d1 %>% 
  filter(task_name == "RV") %>% 
   group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp)) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_fd <- d1 %>% 
  filter(task_name == "FD", resp_type == "first_mention_focal") %>% 
   group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp)) %>% 
  select(subject, culture, task_name, resp_num)

clean_d1_ca <- d1 %>% 
  filter(task_name == "CA", resp_type == "situation_attribution")%>% 
  group_by(subject, culture, task_name) %>% 
  summarise(resp_num = mean(resp)) %>% 
  select(subject, culture, task_name, resp_num)


d1_region_df <- bind_rows(clean_d1_ca, 
          clean_d1_ebb, 
          clean_d1_fd, 
          clean_d1_hz, 
          clean_d1_rmts, 
          clean_d1_rv, 
          clean_d1_ssi, 
          clean_d1_up) %>% 
  left_join(us_d1_region_d %>% select(subject, culture, coast, region), by = c("subject", "culture")) %>% 
  left_join(cn_d1_region_d %>% select(subject, culture, rice_cat), by = c("subject", "culture")) %>% 
   select(subject, culture, task_name, resp_num, rice_cat, coast,region) %>% 
  pivot_longer(cols = c("rice_cat", "coast", "region"), 
               names_to = "region_type", 
               values_to = "region") %>% 
  mutate(region = as.factor(region)) %>% 
  group_by(culture, task_name, region_type) %>% 
  nest() %>% 
  filter(!(culture == "CN" & region_type %in% c("coast", "region")), 
         !(culture == "US"& region_type == "rice_cat")) %>% 
  mutate(mod = case_when(
    region_type == "rice_cat" ~ map(data, function (df) lm(resp_num ~ relevel(region, 
                                                                              ref = 
                                                                              "wheat"),
                                  data = df)),
    region_type == "region" ~ map(data, function (df) lm(resp_num ~ relevel(region, 
                                                                              ref = 
                                                                          "West"),
                                  data = df)),
    region_type == "coast" ~ map(data, function (df) lm(resp_num ~ relevel(region, 
                                                                              ref = 
                                                                          "west_coast"),
                                  data = df))
  ), 
  tidy = map(mod, tidy)) %>% 
  select(-mod, -data) |>
  unnest(cols = c(tidy)) %>% 
  filter(grepl("region", term)) 


d1_region_df <- d1_region_df %>% mutate(p.value_print = 
                                          case_when(
                                            p.value < 0.01 ~ "< 0.01",
                                            TRUE ~ paste0("= ", round(p.value, 2))
                                    
                                          ))

d1_region_df$p.adjusted = p.adjust(d1_region_df$p.value,
                                    method = "bonferroni")

saveRDS(d1_region_df, here("cached_results/ea/d1_region.RDS"))

d1_region_df %>% 
  knitr::kable(digits = 3)
```


## study 2

```{r}
# here we are recycling the code snippet from above so that we can run batch models
d2_region_df <- d2_with_scale  %>% 
  filter(task_name %in% c("RMTS","RV","FD"))  %>% 
  mutate(resp_num = as.numeric(resp))  %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  summarise(resp_num = mean(resp_num)) %>% 
  bind_rows(clean_d2_CD, clean_d2_SSI, clean_d2_CA, 
            clean_d2_TD, clean_d2_SeI) %>% 
  select(-scale_sum_score) %>% 
# start combining the demographic information   
  left_join(cn_d2_region_d %>% select(subject, 
                                      culture, 
                                      rice_cat), by = c("subject", "culture")) %>% 
  left_join( us_d2_region_d %>% select(subject, culture, coast, region), 
             by = c("subject", "culture")) %>% 
  select(subject, culture, task_name, resp_num, rice_cat, coast,region) %>% 
  pivot_longer(cols = c("rice_cat", "coast", "region"), 
               names_to = "region_type", 
               values_to = "region") %>% 
  mutate(region = as.factor(region)) %>% 
  group_by(culture, task_name, region_type) %>% 
  nest() %>% 
  filter(!(culture == "CN" & region_type %in% c("coast", "region")), 
         !(culture == "US"& region_type == "rice_cat")) %>% 
  mutate(mod = case_when(
    region_type == "rice_cat" ~ map(data, function (df) lm(resp_num ~ relevel(region, 
                                                                              ref = 
                                                                              "wheat"),
                                  data = df)),
    region_type == "region" ~ map(data, function (df) lm(resp_num ~ relevel(region, 
                                                                              ref = 
                                                                          "West"),
                                  data = df)),
    region_type == "coast" ~ map(data, function (df) lm(resp_num ~ relevel(region, 
                                                                              ref = 
                                                                          "west_coast"),
                                  data = df))
  ), 
  tidy = map(mod, tidy)) %>% 
  select(-mod, -data) |>
  unnest() %>% 
  filter(grepl("region", term)) 


d2_region_df <- d2_region_df %>% mutate(p.value_print = 
                                          case_when(
                                            p.value < 0.01 ~ "< 0.01",
                                            TRUE ~ paste0("= ", round(p.value, 2))
                                    
                                          ))

d2_region_df$p.adjusted = p.adjust(d2_region_df$p.value,
                                    method = "bonferroni")


saveRDS(d2_region_df, here("cached_results/ea/d2_region.RDS"))


d2_region_df %>% 
  knitr::kable(digits = 3)
```



# Basic demog

first putting the two clean df together 
```{r}
d1_clean <- bind_rows(clean_d1_ca, 
          clean_d1_ebb, 
          clean_d1_fd, 
          clean_d1_hz, 
          clean_d1_rmts, 
          clean_d1_rv, 
          clean_d1_ssi, 
          clean_d1_up) %>% 
  select(subject, culture, task_name, resp_num) 

d2_clean <- d2_with_scale  %>% 
  filter(task_name %in% c("RMTS","RV","FD"))  %>% 
  mutate(resp_num = as.numeric(resp))  %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  summarise(resp_num = mean(resp_num)) %>% 
  bind_rows(clean_d2_CD, clean_d2_SSI, clean_d2_CA, 
            clean_d2_TD, clean_d2_SeI) %>% 
  select(subject, culture, task_name, resp_num) 

d12_joint_df <- bind_rows(d1_clean %>% mutate(study = "d1"), 
          d2_clean %>% mutate(study = "d2")) 

```


```{r}
cleaned_basic_demog_df <- 
bind_rows(d1_demog %>% mutate(study = "d1"),
          d2_demog %>% mutate(study = "d2")) %>% 
  mutate(demog_response = case_when(
    demog_response == "没有国际经历" ~ "No experiences",
    demog_response == "一段国际经历" ~ "One experience",
    demog_response == "两段国际经历" ~ "Two experiences",
    demog_response == "三到五段国际经历" ~ "Three to five experiences",
    demog_response == "六段或更多国际经历" ~ "Six or more experiences", 
    TRUE ~ demog_response
  )) %>% 
  mutate(demog_response = case_when(
    demog_response == "No experiences" ~ "0", 
    demog_response ==  "One experience" ~ "1",
    demog_response == "Two experiences" ~ "2",
    demog_response ==  "Three to five experiences" ~ "3",
    demog_response ==  "Six or more experiences" ~ "4", 
    
    demog_response %in% c('8th grade/junior high or less', 
                          "九年级/初中及以下") ~ "0",
      
    demog_response %in% c('Some high school', 
                           "上过一部分高中") ~ "1",
      
    demog_response %in% c('High school graduate/GED', 
                          "普通高中或职业高中毕业/高中等级学历") ~"2",
    
    
    demog_response %in% c('One or more years of college, no degree', 
                          "一年或多年大学教育，无学位") ~ "3",
    
    demog_response %in% c('Two-year college degree/vocational school', 
                          "大专学历") ~ "4",
    
    demog_response %in% c("Four-/Five-year college Bachelor's degree", 
                          "四年/五年制大学本科学位") ~ "5", 
    
     demog_response %in% c("At least some graduate school", 
                          "有过一些研究生经历") ~ "6", 
    
    TRUE ~ demog_response
  ))
```


- numeric: 
resimobinum 
overseaexpnum
objectiveses - s1 only
subjectiveses 
age

- category:
gender 
stem_or_not s2 only

## numeric demog 

```{r}
# a small proportion of people responded in a way that's difficult to code 
# here we exclude them 
resimobinum_exclusion <- bind_rows(d1_demog, d2_demog) %>% 
  filter(demog_question == "resimobinum") %>% 
  mutate(demog_response_num = as.numeric(demog_response)) %>% 
  filter(is.na(demog_response_num)) %>% 
  pull(subject)


demog_d12_numeric_df <- d12_joint_df %>% 
  left_join(cleaned_basic_demog_df, 
            by = c("subject", "culture", "study")) %>% 
  rename(demog_type = demog_question) %>% 
  filter(demog_type %in% c("overseaexpnum", "objectiveses","subjectiveses", "age", 
                           "resimobinum")) %>% 
  mutate(demog_resp = as.numeric(demog_response)) %>% 
  filter(!(subject %in% resimobinum_exclusion & demog_type == "resimobinum"))


demog_d12_numeric_mod <- demog_d12_numeric_df %>% 
  group_by(culture, task_name, study, demog_type) %>% 
  nest() %>% 
  mutate(mod = map(data, function (df) lm(resp_num ~ demog_resp, data = df)), 
         tidy = map(mod, tidy)) %>% 
  select(-mod, -data) %>% 
  unnest(cols = c(tidy))



demog_d12_numeric_mod %>% 
  filter(term != "(Intercept)") %>% 
  knitr::kable(digits = 3)
```

## categorical demog 

```{r}
demog_d12_cat_df <- d12_joint_df %>% 
  left_join(cleaned_basic_demog_df, 
            by = c("subject", "culture", "study")) %>% 
  rename(demog_type = demog_question) %>% 
  filter(demog_type %in% c("gender", "stem_or_not"))


demog_d12_cat_mod <- demog_d12_cat_df %>% 
  group_by(culture, task_name, study, demog_type) %>% 
  nest() %>% 
  mutate(mod = map(data, function (df) lm(resp_num ~ demog_response, data = df)), 
         tidy = map(mod, tidy)) %>% 
  select(-mod, -data) %>% 
  unnest(cols = c(tidy))


demog_d12_cat_mod %>% 
  filter(term != "(Intercept)") %>% 
  knitr::kable(digits = 3)
```



```{r}
demog_d12_mod <- bind_rows(demog_d12_cat_mod, demog_d12_numeric_mod)
demog_d12_mod$p.adjusted = p.adjust(demog_d12_mod$p.value,
          method = "bonferroni")

saveRDS(demog_d12_mod, here("cached_results/ea/d12_demog_df.RDS"))
```


# select the non-corrected one

```{r}
demog_d12_mod <- readRDS(here("cached_results/ea/d12_demog_df.RDS"))
 
demog_d12_mod %>% 
  filter(p.value < .05, term != "(Intercept)") %>%
  filter(!demog_type %in% c("gender", "age", "objectiveses")) %>% 
  arrange(demog_type)
```

# Maternal education binned version


```{r}

cat_objective_ses_df <- d12_joint_df %>% 
  left_join(cleaned_basic_demog_df, 
            by = c("subject", "culture", "study")) %>% 
  rename(demog_type = demog_question) %>% 
  filter(demog_type == "objectiveses") %>% 
  ungroup() %>% 
  mutate(objectiveses_cat = if_else(demog_response > 3, "high", "low")) %>% 
  select(culture, task_name, study, subject, objectiveses_cat, resp_num)

categorical_variable <- cat_objective_ses_df %>% 
  group_by(culture, task_name, study) %>% 
    nest() %>% 
  mutate(mod = map(data, function (df) lm(resp_num ~ objectiveses_cat, data = df)), 
         tidy = map(mod, tidy)) %>% 
  select(-mod, -data) %>% 
  unnest(cols = c(tidy))

categorical_variable %>%
  filter(p.value < 0.05)

```

# Counting region each number of participants 

```{r}
d1_coast_us_by_task_df <- bind_rows(clean_d1_ca, 
          clean_d1_ebb, 
          clean_d1_fd, 
          clean_d1_hz, 
          clean_d1_rmts, 
          clean_d1_rv, 
          clean_d1_ssi, 
          clean_d1_up) %>% 
  left_join(us_d1_region_d %>% select(subject, culture, coast, region), by = c("subject", "culture")) %>% 
  left_join(cn_d1_region_d %>% select(subject, culture, rice_cat), by = c("subject", "culture")) %>% 
   select(subject, culture, task_name, resp_num, rice_cat, coast,region) %>% 
  distinct(subject, task_name, coast, region, rice_cat, culture) %>% 
  ungroup() %>% 
  group_by(coast, culture, task_name) %>% 
  count() %>% 
  filter(culture != "CN")

d1_region_us_by_task_df <- bind_rows(clean_d1_ca, 
          clean_d1_ebb, 
          clean_d1_fd, 
          clean_d1_hz, 
          clean_d1_rmts, 
          clean_d1_rv, 
          clean_d1_ssi, 
          clean_d1_up) %>% 
  left_join(us_d1_region_d %>% select(subject, culture, coast, region), by = c("subject", "culture")) %>% 
  left_join(cn_d1_region_d %>% select(subject, culture, rice_cat), by = c("subject", "culture")) %>% 
   select(subject, culture, task_name, resp_num, rice_cat, coast,region) %>% 
  distinct(subject, task_name, coast, region, rice_cat, culture) %>% 
  ungroup() %>% 
  group_by(region, culture, task_name) %>% 
  count() %>% 
  filter(culture != "CN")

d1_us_region_coast_df <- bind_rows(d1_coast_us_by_task_df, d1_region_us_by_task_df) %>% 
  mutate(exp = "experiment1")



d2_coast_us_by_task_df <- d2_with_scale  %>% 
  filter(task_name %in% c("RMTS","RV","FD"))  %>% 
  mutate(resp_num = as.numeric(resp))  %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  summarise(resp_num = mean(resp_num)) %>% 
  bind_rows(clean_d2_CD, clean_d2_SSI, clean_d2_CA, 
            clean_d2_TD, clean_d2_SeI) %>% 
  select(-scale_sum_score) %>% 
# start combining the demographic information   
  left_join(cn_d2_region_d %>% select(subject, 
                                      culture, 
                                      rice_cat), by = c("subject", "culture")) %>% 
  left_join( us_d2_region_d %>% select(subject, culture, coast, region), 
             by = c("subject", "culture")) %>% 
  select(subject, culture, task_name, resp_num, rice_cat, coast,region) %>% 
  ungroup() %>% 
   distinct(subject, task_name, coast, region, rice_cat, culture) %>% 
  ungroup() %>% 
  group_by(coast, culture, task_name) %>% 
  count() %>% 
  filter(culture != "CN")

d2_region_us_by_task_df <- d2_with_scale  %>% 
  filter(task_name %in% c("RMTS","RV","FD"))  %>% 
  mutate(resp_num = as.numeric(resp))  %>% 
  group_by(subject, culture, task_name, scale_sum_score) %>% 
  summarise(resp_num = mean(resp_num)) %>% 
  bind_rows(clean_d2_CD, clean_d2_SSI, clean_d2_CA, 
            clean_d2_TD, clean_d2_SeI) %>% 
  select(-scale_sum_score) %>% 
# start combining the demographic information   
  left_join(cn_d2_region_d %>% select(subject, 
                                      culture, 
                                      rice_cat), by = c("subject", "culture")) %>% 
  left_join( us_d2_region_d %>% select(subject, culture, coast, region), 
             by = c("subject", "culture")) %>% 
  select(subject, culture, task_name, resp_num, rice_cat, coast,region) %>% 
  ungroup() %>% 
   distinct(subject, task_name, coast, region, rice_cat, culture) %>% 
  ungroup() %>% 
  group_by(region, culture, task_name) %>% 
  count() %>% 
  filter(culture != "CN")

d2_us_region_coast_df <- bind_rows(d2_coast_us_by_task_df, d2_region_us_by_task_df) %>% 
   mutate(exp = "experiment2")

us_region_coast_n_df <- bind_rows(d1_us_region_coast_df, d2_us_region_coast_df) %>% 
  filter(!(is.na(coast) & is.na(region)))

saveRDS(us_region_coast_n_df, here("cached_results/ea/d12_us_region_coast_n_df.Rds"))
```


