---
title: "bf investigation"
author: "anjie"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(here)
library(bridgesampling)
library(rstanarm)
library(brms)
library(broom)
library(broom.mixed)

```

here we use the SSI task as an example because its models runs fast 

```{r}
d2 <- read_csv(here("data/03_processed_data/exp2/tidy_main.csv"))
ssi_df <- d2 %>% 
  filter(task_name == "SSI") %>% 
  filter(resp_type == "task_score_ratio") %>% 
  mutate(score = as.numeric(resp)) %>% 
  select(-resp, -task_info, -trial_info, -resp_type)


```

# variations in BF

first we want to run models with recommended posterior sample size: 1e+05

```{r}
full_ssi_model <-  rstanarm::stan_glm(
    score ~ culture, 
    data = ssi_df, 
    iter = 10000, 
    warmup = 1000,
    diagnostic_file = file.path(tempdir(), "df.csv"))

null_ssi_model <-  rstanarm::stan_glm(
    score ~ 1, 
    data = ssi_df, 
    #iter = 50000,
    diagnostic_file = file.path(tempdir(), "df.csv"))


saveRDS(full_ssi_model, here("processing_pipelines/misc/full_ssi_model_ideal.RDS"))
saveRDS(null_ssi_model, here("processing_pipelines/misc/null_ssi_model_ideal.RDS"))

summary(full_ssi_model)
summary(null_ssi_model)
```

then run bf muliple times. it still gave warning
it's all zero

```{r}
# caching is obviously not working because they way the diagnostics files are handled
#full_ssi_model <- readRDS(here("processing_pipelines/misc/full_ssi_model_ideal.RDS"))
#null_ssi_model <-  readRDS(here("processing_pipelines/misc/null_ssi_model_ideal.RDS"))


multiple_bf <- tibble(
  id = seq(1, 20, 1)
) %>% 
  mutate(bf = map(., function(x){
    bayes_factor(bridge_sampler(full_ssi_model), 
                 bridge_sampler(null_ssi_model))$bf
  }))


l <- lapply(seq(1, 20, 1), function(x){
  bayes_factor(bridge_sampler(full_ssi_model), 
                 bridge_sampler(null_ssi_model))$bf
})
```

# variations by samples 

```{r}

exp_with_sample <- function(s){
  full_ssi_model <-  rstanarm::stan_glm(
    score ~ culture, 
    data = ssi_df, 
    iter = s,
    diagnostic_file = file.path(tempdir(), "df.csv"))
  
  null_ssi_model <-  rstanarm::stan_glm(
    score ~ 1, 
    data = ssi_df, 
    iter = s,
    diagnostic_file = file.path(tempdir(), "df.csv"))
  
  bf = bayes_factor(bridge_sampler(full_ssi_model), 
                    bridge_sampler(null_ssi_model))$bf
  
  res = broom.mixed::tidy(full_ssi_model) %>% 
    mutate(sample = s, 
           bf = bf)
  
  return (res)
}


a <- lapply(seq(5000, 50000, 1000), 
       function(x){
         exp_with_sample(x)
       }) %>% 
  bind_rows()

```

similarly, stable estimate, similar bf and no change
```{r}
saveRDS(a, "exp_with_sample_bf.RDS")

a <- readRDS("exp_with_sample_bf.RDS")
a
```


# compare brms and rstanarm 

```{r}
# first building the no random effects version
get_prior_from_rstanarm <- function(model){
  
  fixed_effect_prior = paste0(
    (prior_summary(model)$prior)$dist,
    "(",
    (prior_summary(model)$prior)$location,
    ",",
    (prior_summary(model)$prior)$adjusted_scale,
    ")")
  
  return (fixed_effect_prior)
}

get_prior_intercept_from_rstanarm <- function(model){
  intercept_prior = paste0(
    (prior_summary(model)$prior_intercept)$dist,
    "(",
    (prior_summary(model)$prior_intercept)$location,
    ",",
    (prior_summary(model)$prior_intercept)$adjusted_scale,
    ")")
  
  return (intercept_prior)
}

get_prior_aux_from_rstanarm <- function(model){
  intercept_prior = paste0(
    (prior_summary(model)$prior_aux)$dist,
    "(",
    "rate = ", 
    (prior_summary(model)$prior_aux)$rate /(prior_summary(model)$prior_aux)$adjusted_scale  , 
    ")")
  
  return (intercept_prior)
}


ssi_priors <- c(
  set_prior(get_prior_from_rstanarm(full_ssi_model), 
            class = "b", coef = "cultureUS"),
  set_prior(get_prior_intercept_from_rstanarm(full_ssi_model), 
            class = "Intercept")#,
  #set_prior(get_prior_aux_from_rstanarm(full_ssi_model), 
     #        class = "sigma")
 
)

brms_full <-  brms::brm(
    score ~ culture,
    prior = ssi_priors, 
    data = ssi_df)

brms_null <- brms::brm(
    score ~ 1,
    prior = c(set_prior(get_prior_intercept_from_rstanarm(full_ssi_model), 
            class = "Intercept")), 
    data = ssi_df)
```

4000 posterior sample, note the culture's CI doesn't include zero


```{r}
summary(brms_full)
tidy(brms_full)
```

can't run, abort R all the time 

```{r}
bayes_factor(brms_full, brms_null)
```

```{r}
brms_full_default <-  brms::brm(
    score ~ culture,
    data = ssi_df)

brms_null_default <- brms::brm(
    score ~ 1,
    data = ssi_df)
```



