---
output:
  pdf_document: default
  html_document: default
---
```{r}
library(tidyverse)
library(here)
library(papaja)
library(kableExtra)
library(glue)

d1 <- read_csv(here("data/03_processed_data/exp1/tidy_main.csv"))
d2 <- read_csv(here("data/03_processed_data/exp2/tidy_main.csv"))

```

\begin{longtable}{l p{1.2in} p{1.4in} p{1.4in} p{.2in} p{.2in}}
    \caption{Tasks included in each experiment and the final sample size after exclusion.}\\
    \small  % Switch from 12pt to 11pt; otherwise, table won't fit
    \setlength\LTleft{0pt}            
    \setlength\LTright{0pt}         
    
    \bf{Experiment} & \bf{Task} & \bf{Citation} & \bf{Task Description} & \bf{CN} & \bf{US} \\
    \hline
        1 & Ambiguous Relational Match-To-Sample (RMTS) & Carstensen et al. (2019) & Infer whether an object or relation is causally relevant &  167  &  169 \\

& Picture Free Description & Imada, Carlson, \& Ktakura (2013) & Describe pictures from memory after a brief study period &  167 &  169\\

& Ebbinghaus Illusion & Imada, Carlson, \& Itakura (2013) & Judge the size of circles in a context designed to bias size judgments &  167  &  169\\

& Horizon Collage & Senzaki, Masuda, \& Nand (2014) & Make an image by dragging and dropping stickers onto a display &  167  &  169\\

& Symbolic Self-Inflation (Family) & Kitayama et al. (2009) & Draw self and family members as circles &  141 &  110\\

& Uniqueness Preference & Kim \& Markus (1999) & Choose a sticker from five stickers, four of which are the same color &  167 &  169\\

& Child Causal Attribution & Seiver, Gopnik, \& Goodman (2013) & Watch short vignettes and explain the decisions of the characters &  167 &  169\\

& Raven's Progressive Matrices & Su (2020) & Use analogic reasoning to complete visually-presented patterns &  167 &  169\\
2 & Ambiguous Relational Match-To-Sample (RMTS) & Carstensen et al. (2019) & Infer whether an object or relation is causally relevant &  174 &  293\\

& Picture Free Description & Imada, Carlson, \& Itakura (2013) & Describe pictures from memory after a brief study period &  132 &  284\\

& Change Detection & Mausda \& Nisbett (2007) & Find differences in the foreground or background of two images &  160 &  253\\

& Symbolic Self-Inflation (Friends) & Kitayama et al. (2009) & Draw a sociogram with self and friends as nodes, relationships as edges &  158 &  252\\

& Adult Causal Attribution & Morris \& Peng (1994) & Read a crime story and explain the criminal’s motivations &  114 &  293\\

& Taxonomic-Thematic Similariy & Ji, Zhang, \& Nisbett (2004) & Match items based on taxonomic or thematic similarity (e.g., cow: chicken / grass) & 178 &  295\\

& Semantic Intuition & Li, Liu, Chalmers, \& Snedeker (2018) & Decide whether a story refers to a named character (whose actions are mischaracterized) or the person who performed the actions (but had a different name) &  181 &  298\\

& Raven's Progressive Matrices & Su (2020) & Use analogical reasoning to complete visually-presented patterns &  181 &  298\\
    \hline
    \end{longtable}

# table 2



\begin{longtable}{l p{1.2in} p{1.4in} p{1.4in} p{.2in} p{.2in}}
    \caption{Tasks included in each experiment and the final sample size after exclusion.}\\
    \small  % Switch from 12pt to 11pt; otherwise, table won't fit
    \setlength\LTleft{0pt}            
    \setlength\LTright{0pt}         
    
    \bf{Task Name} & \bf{Difference between the current version and the original version} & \bf{Speculative reasons} \\
    \hline
        1 & Ambiguous Relational Match-To-Sample (RMTS) & Carstensen et al. (2019) & Infer whether an object or relation is causally relevant &  167  &  169 \\

& Picture Free Description & Imada, Carlson, \& Ktakura (2013) & Describe pictures from memory after a brief study period &  167 &  169\\

& Ebbinghaus Illusion & Imada, Carlson, \& Itakura (2013) & Judge the size of circles in a context designed to bias size judgments &  167  &  169\\

& Horizon Collage & Senzaki, Masuda, \& Nand (2014) & Make an image by dragging and dropping stickers onto a display &  167  &  169\\

& Symbolic Self-Inflation (Family) & Kitayama et al. (2009) & Draw self and family members as circles &  141 &  110\\

& Uniqueness Preference & Kim \& Markus (1999) & Choose a sticker from five stickers, four of which are the same color &  167 &  169\\

& Child Causal Attribution & Seiver, Gopnik, \& Goodman (2013) & Watch short vignettes and explain the decisions of the characters &  167 &  169\\

& Raven's Progressive Matrices & Su (2020) & Use analogic reasoning to complete visually-presented patterns &  167 &  169\\
2 & Ambiguous Relational Match-To-Sample (RMTS) & Carstensen et al. (2019) & Infer whether an object or relation is causally relevant &  174 &  293\\

& Picture Free Description & Imada, Carlson, \& Itakura (2013) & Describe pictures from memory after a brief study period &  132 &  284\\

& Change Detection & Mausda \& Nisbett (2007) & Find differences in the foreground or background of two images &  160 &  253\\

& Symbolic Self-Inflation (Friends) & Kitayama et al. (2009) & Draw a sociogram with self and friends as nodes, relationships as edges &  158 &  252\\

& Adult Causal Attribution & Morris \& Peng (1994) & Read a crime story and explain the criminal’s motivations &  114 &  293\\

& Taxonomic-Thematic Similariy & Ji, Zhang, \& Nisbett (2004) & Match items based on taxonomic or thematic similarity (e.g., cow: chicken / grass) & 178 &  295\\

& Semantic Intuition & Li, Liu, Chalmers, \& Snedeker (2018) & Decide whether a story refers to a named character (whose actions are mischaracterized) or the person who performed the actions (but had a different name) &  181 &  298\\

& Raven's Progressive Matrices & Su (2020) & Use analogical reasoning to complete visually-presented patterns &  181 &  298\\
    \hline
    \end{longtable}



```{r eval=FALSE, include=FALSE}
data.frame(
  `Task Name` = c("Ambiguous Relational Match-To-Sample", 
                  "Ebbinghaus Illusion", 
                  "Horizon Collage", 
                  "Symbolic Self-Inflation (Family version and Friends version)", 
                  "Uniqueness Preference", 
                  "Child Causal Attribution", 
                  "Change Detection"), 
  `Difference between the current version and the original version` = c(
    "Age: The original experiment was conducted with young children; the current experiment was conducted with adults.
    Test Format: The original experiment was conducted in person with physical stimuli and live experimenters; the current experiment was conducted through web-based interfaces with animation.", 
   "Age: The original study was conducted with young children; the current experiment was conducted with adults.
    Culture: The original experiment compared Japanese participants with Canadian participants; the current experiment compared Chinese participants with U.S. participants.", 
   "Age: The original experiment was conducted with young children; the current experiment was conducted with adults.
    Test Format: The original experiment was conducted in person with canvas and collage stickers; the current experiment was conducted through web-based interfaces.
    Culture: The original experiment compared Japanese participants with Canadian participants; the current experiment compared Chinese participants with U.S. participants.", 
   "Test Format: The original experiment was conducted in person with pen and paper; the current experiment was conducted through web-based interfaces.
   Test Prompt: The original experiment asked the participants to draw their close social network; the current experiment asked the participants to draw their family members or friends growing up.", 
   "Test Format: The original experiment was conducted in person; the current experiment was conducted through web-based interfaces.
   Stimulus: The original experiment was giving away physical pens; the current experiment was asking the participants to select virtual stickers.", 
   "Age: The original experiment was conducted with young children; the current experiment was conducted with adults.", 
   "Test Format: The original experiment was conducted in person; the current experiment was conducted through web-based interfaces."
  ), 
  `Speculative reasons` = c(
    "The relation between objects might have been less salient when the stimuli were presented as schematic animation.
     Adults may have been  overall less engaged with the tasks and paid less attention to the causal properties of the object pairs.", 
    "Adults in both cultures reached ceiling performance. 
    U.S. and Chinese participants may different levels of visual context sensitivity compared to Canadian and Japanese participants.", 
    "The task might have been too trivial for adults to engage with properly. 
    The saliency of horizon height is diminished by the drag-and-drop online interface. ", 
    "The online interface might have altered participants’ drawing process, making it more difficult to implicitly represent the symbolic meaning of the circle size.", 
    "The choice for a virtual sticker represents is less meaningful than a choice for a real pen.
    The presence of a live experimenter might increase the social pressure on participants, causing them to consider the cultural perception of their choice. ", 
    "Adults may have failed to engage with their causal reasoning because the story is too simplistic. ", 
    "The in-lab setting might facilitate participants’ performance by making them pay more attention to the computer screen. "
  )
) %>% 
  kable( "latex", align = "l", longtable  = TRUE,
      row.names = FALSE,
       col.names = c("Task Name",
                    "Difference between the current version and the original version",
                    "Speculative reasons")) %>%
kable_styling(full_width = TRUE,
              bootstrap_options = c("condensed"))

```


