
```{r}
cor_tasks <- readRDS(here("cached_results/ea/cor_main_df.RDS"))

```


One (perhaps simplistic) interpretation of the prior literature on cultural variation is that there is a general tendency toward holistic or analytic reasoning that varies across cultures and explains variation in tasks. This single dimension might correspond to broad (or focused) attention and contextualized, relational reasoning (or an emphasis on focal people or objects). As a first step towards investigating this interpretation, we explored whether there was a single dimension of cross-cultural variation in our data. We treated the missing data using two approaches: listwise deletion and imputation with means. Two approaches yielded comparable results with the correlation values, so here we reported correlations from listwise deletion. 

```{r}

max_cor_df <- cor_tasks %>% 
  filter(task_1 != task_2) %>% 
  filter(missing_data == "deleted") %>% 
  arrange(-abs(value)) %>% 
  head(6)

```


Correlations between task scores were quite low on average, however, suggesting limited support for this hypothesis. Across both Experiments 1 and 2, the largest correlations observed were `r round(filter(max_cor_df, task_1 == "TD", task_2 == "CA")$value, 2)` (Triads and Adult Causal Attribution in study 2) and `r round(filter(max_cor_df, task_1 == "FD", task_2 == "RV")$value, 2)` (Free Description and Ravens in Study 2), and `r round(filter(max_cor_df, task_1 == "CA", task_2 == "FD")$value, 2)` (Adult Causal Attribution and Free Description in Study 2) All other correlations were between -0.23 and 0.23. Hence, the amount of shared variation between tasks was quite limited and our attempts at exploratory factor analysis discovered structures with many distinct factors and very low loading on the first factor. We did not pursue this direction further though we welcome further explorations of this type using our dataset. 


