
```{r}
task_gi_scale_df <- readRDS(here("cached_results/ea/task_giscale_df.RDS"))
d1_region_df <- readRDS(here("cached_results/ea/d1_region.RDS"))
d2_region_df <- readRDS(here("cached_results/ea/d2_region.RDS"))
d12_numeric_demog_df <- readRDS(here("cached_results/ea/d12_numeric_demog_df.RDS"))
d12_cat_demog_df <- readRDS(here("cached_results/ea/d12_cat_demog_df.RDS"))
```

Does demographic or variation in cultural identity predict responding in our tasks? Our approach to this question was to fit a set of exploratory regression models for each task, predicting task scores as a function of an individual scale and its interaction with culture. This approach allowed us to explore both within- and across-culture effects in a single model. Our predictors were 1) the summed score for our global/local cultural identity and consumption measures (with local items reverse-scored, such that higher scores represent more global identity and consumption patterns), 2) geographic information about where participants grew up (specifically, regions that have historically farmed primarily rice or wheat in China, following [-@talhelm2014large], and culturally distinct regions of the US following FIXME), and 3) a range of demographic factors, [FIXME] including age, gender identity, subjective socioeconomic status measured using the MacArthur Ladder, level of maternal education, residential mobility[FIXME], and number of international experiences. 

### Task-Global identity relationships 

```{r eval=FALSE, include=FALSE}
task_gi_scale_df %>% 
  filter(p.value < .05)
```

We fit the global-local identity models for tasks in Experiment 2 since we did not collect these scales in Experiment 1. We include the coefficients for all models in Supplementary Table FIXME Two of these relationships were statistically significant at .01 < p < .05 (Adult Causal Attribution task and Triads task) but neither of these relationships were particularly strong and they would not survive any appropriate correction for multiple comparisons. 

### Task-Geographic origin relationships 

```{r eval=FALSE, include=FALSE}
d1_region_df %>% 
  filter(p.value < .05)

d2_region_df %>% 
  filter(p.value < .05)
```

We considered whether regions within each country were meaningful predictors for task performance. For China, regions were categorized as rice-cultivating regions and wheat-cultivating regions based on FIXME. For U.S. regions were categorized as either FIXME. We fit the region models for tasks in Experiment 1 and Experiment 2 separately, and coefficients for all models were included in the Supplementary Table FIXME. One relationship in Experiment 1 (Coast for Free Description in U.S) and four relationships in Experiment 2 (Coast and Region for Ravens in U.S; Coast and Region for Change Detection in U.S) were statistically significant at  .01 < p < .05. But none survived Bonferroni correction for multiple comparisons. 

### Basic demographic effects

```{r}
c(unique(d12_numeric_demog_df$demog_type),
unique(d12_cat_demog_df$demog_type))

d12_numeric_demog_df %>% 
  filter(!grepl("Intercept", term)) %>% 
  filter(p.value < 0.05) %>% 
  arrange(demog_type)

d12_cat_demog_df %>% 
  filter(!grepl("Intercept", term)) %>% 
  filter(p.value < 0.05) %>% 
  arrange(demog_type)


d12_numeric_demog_df %>% 
  filter(!grepl("Intercept", term)) %>% 
  filter(p.adjusted < 0.05) %>% 
  arrange(demog_type)

d12_cat_demog_df %>% 
  filter(!grepl("Intercept", term)) %>% 
  filter(p.adjusted < 0.05) %>% 
  arrange(demog_type)
```





