
```{r}
task_gi_scale_df <- readRDS(here("cached_results/ea/task_giscale_df.RDS"))
d1_region_df <- readRDS(here("cached_results/ea/d1_region.RDS"))
d2_region_df <- readRDS(here("cached_results/ea/d2_region.RDS"))
d12_demog_df <- readRDS(here("cached_results/ea/d12_demog_df.RDS"))
```

As a final exploratory analysis, we asked whether demographic variation or variation in cultural identity predicted responding in our tasks. Our approach to these questions was to fit a set of exploratory regression models for each task, predicting task scores as a function of an individual scale and its interaction with culture. This approach allowed us to explore both within- and between-culture effects in a single model. Our predictors were 1) the summed score for our global/local cultural identity and consumption measures (with local items reverse-scored, such that higher scores represent more global identities and consumption patterns); 2) geographic information about where participants grew up [specifically, regions that have historically farmed primarily rice or wheat in China, following @talhelm2014large, and culturally distinct regions of the US following @markus2014clash]; and 3) a range of demographic factors, including age, gender identity, residential mobility, number of international experiences, maternal education level, and subjective socioeconomic status as measured by the MacArthur Ladder [@adler2000relationship]. 

### Task performance and global identity 

```{r eval=FALSE, include=FALSE}
task_gi_scale_df %>% 
  filter(p.value < .05)
```

We fit models predicting task performance based on culture and its interaction with global (vs local) identity for tasks in Experiment 2 (we did not collect these scales in Experiment 1). Two of these relationships were statistically significant at .01 < p < .05 (Adult Causal Attribution: *p* = `r round(filter(task_gi_scale_df, task_name == "CA", grepl("cultureUS", term))$p.value, 2)`; Taxonomic-Thematic Similarity: *p* = `r round(filter(task_gi_scale_df, task_name == "TD", grepl("cultureUS", term))$p.value, 2)`) but neither of these relationships survived Bonferroni correction for multiple comparisons. 

### Task performance and geographic origin 

```{r include=FALSE}
n_task_geo_models <- nrow(bind_rows(d1_region_df %>% mutate(study = "study1"), 
          d2_region_df %>% mutate(study = "study2")) %>% 
  distinct(culture, task_name, region_type, study)) 


n_sig_geo_models <- nrow(bind_rows(d1_region_df %>% mutate(study = "study1"), 
          d2_region_df %>% mutate(study = "study2")) %>% 
        filter(p.value < .05) %>% 
  distinct(culture, task_name, region_type, study)) 
d1_region_df %>% 
  filter(p.value < .05)

d2_region_df %>% 
  filter(p.value < .05)
```

We next considered whether regions within each country were meaningful predictors of task performance. We fit models predicting task performance based on the regions that participants reported growing up in. For China, provinces were categorized as rice-cultivating regions or wheat-cultivating regions based on @talhelm2014large. For the US, states were categorized based on either the coastal locations (West Coast, East Coast, and Inland) or broad geographic locations (West, South, Northeast, Midwest), following the categorization reported in @carstensen2022bridging. 

`r n_sig_geo_models` out of the `r n_task_geo_models` models we ran showed statistically significant relationships between regions and task performance. In Experiment 1, US coastal location was a significant predictor for the Free Description task. Participants who grew up in Inland regions or on the East Coast were more likely to mention the focal object first when describing the pictures (Inland: *p* `r (d1_region_df %>% filter(task_name == "FD") %>% filter(grepl("inland", term)))$p.value_print`; East Coast: *p* `r (d1_region_df %>% filter(task_name == "FD") %>% filter(grepl("east_coast", term)))$p.value_print`). In Experiment 2, both coastal location and broad geographic location were significant predictors for Raven's SPM, with participants from the East Coast and Inland regions scoring higher than participants from the West Coast (Inland: *p* `r (d2_region_df %>% filter(task_name == "RV") %>% filter(grepl("inland", term)))$p.value_print`; East Coast: *p* `r (d2_region_df %>% filter(task_name == "RV") %>% filter(grepl("east_coast", term)))$p.value_print`), and participants from the Midwest and South scoring higher than participants from the West (Midwest: *p* `r (d2_region_df %>% filter(task_name == "RV") %>% filter(grepl("Midwest", term)))$p.value_print`; South: *p* `r (d2_region_df %>% filter(task_name == "RV") %>% filter(grepl("South", term)))$p.value_print`). In addition, both region categories predicted performance in Change Detection. East Coast participants took longer to respond than West Coast participants (*p* `r (d2_region_df %>% filter(task_name == "CD") %>% filter(grepl("east_coast", term)))$p.value_print`), and Northeastern participants took longer to respond than participants who grew up in the West (*p* `r (d2_region_df %>% filter(task_name == "CD") %>% filter(grepl("Northeast", term)))$p.value_print`). However, none of these relationships survived Bonferroni correction. 

### Basic demographic effects

```{r}
n_demog_models <- nrow(d12_demog_df %>% 
  distinct(culture, study, task_name, demog_type))

n_sig_demog_models <- nrow(d12_demog_df %>%
  filter(p.value < .05, !grepl("Intercept", term)) %>% 
  distinct(culture, study, task_name, demog_type)) 
  
```

We fit `r n_demog_models` exploratory regression models to see if basic demographic factors could predict task performance. The demographic factors we explored were age, gender identity, residential mobility, number of international experiences, maternal education level, and subjective socioeconomic status as measured by the MacArthur Ladder [@adler2000relationship]. `r n_sig_demog_models` were statistically significant, but only one model survived Bonferroni correction. Change detection was predicted by age in the US sample, with older participants taking longer to respond than younger participants (adjusted *p* < 0.01).




