```{r}
demog_d12_mod <- readRDS(here("cached_results/ea/d12_demog_df.RDS"))
 
demog_print <- demog_d12_mod %>% 
  filter(p.value < .05, term != "(Intercept)") %>%
  filter(!demog_type %in% c("gender", "age")) %>% 
  arrange(demog_type) %>% 
  select(culture, study, task_name, estimate, std.error, statistic, p.value)
```


# Demographic variation in responses 

In the exploratory analysis section, we explored how basic demographic variables could moderate the task performances within each culture. To do so, we fit an fixed effect model predicting each task's response in each culture, with each demographic variable as the predictor. We fit 192 exploratory regression models in total. 26 models were statistically significant, but only 1 survived Bonferroni correction. However, given that some of the demographic variables have been previously found to moderate task performance, we can  treat this post-hoc exploratory analysis as a proxy for a conceptual replication. Therefore, we report selected uncorrected model results that are significant for key demographic variables in the tables below. These results should be interpreted with great cautions. 


## Residential Mobility 

Higher residential mobility has been found to be related to individual's stronger emphasis on the independent self over the inter-dependent self [@oishi2022socio; @ishii2020residential]. In our exploratory analysis's uncorrected models, residential mobility is a significant predictor to three task responses: U.S. participants' accuracy of Ebbinghaus Illusion task for U.S. participants, Chinese participants' proportion of first mention being focal objects in the Free Description task in Experiment 2, and U.S. participants' proportion of the taxonomic match selection in the Taxonomic-Thematic Similarity task. We reported the model results below. 


```{r}
rm_table <- demog_print %>% 
  filter(demog_type == "resimobinum") %>% 
  mutate(
    study = case_when(
    study == "d1" ~ "Experiment 1", 
    study == "d2" ~ "Experiment 2"
    ), 
    task_name = case_when(
      task_name == "EBB" ~ "Ebbinghaus Illusion", 
      task_name == "FD" ~ "Free Description", 
      task_name == "TD" ~ "Taxonomic-Thematic Similarity" 
    )
  ) %>% 
  rename(
    Study = study, 
    Culture = culture, 
    `Task Name` = task_name, 
    `Beta` = estimate, 
    SE = std.error, 
    t = statistic, 
    p = p.value
  ) %>% 
  ungroup() %>% 
  select(-demog_type) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  select(Study, Culture, `Task Name`, Beta, SE, t, p)


rm_table %>% 
  kable(format = "latex", linesep = '') %>% 
  kable_styling(full_width = F,
                font_size = 9.5)
```


## Socioeconomic Status

### MacArthur Ladder 

The MacAuthur ladder scale is a subjective measure of socioeconomic status [@adler2000relationship]. This measurement has been found to show moderate relationship with the objective socioeconomic measurements, and it has even more robust relationship to individual's subjective well beings than objective socioeconomic measurements [@tan2020association]. Past work has used this measure to investigate the relationship between socioeconomic status and individual's independent versus interdependent orientation [e.g., @miyamoto2018culture]. In our current study, this measure was a significant predictor for five different tasks across two studies. In experiment 1,  MacArthur Ladder scale response was negatively correlated with the proportion of participants choosing the unique pen in the U.S. participants. In experiment 2,  this measure is negatively associated with the relational match Chinese participants selected in the Causal RMTS task, the score U.S. participants received in the Raven's Progressive Matrices, Chinese participants' reaction time in the Change Detection task, and the proportion of taxonomic-match Chinese participants selected in the Taxonomic-Thematic Similarity task. Theses results were summarized in the table below. 


```{r}
demog_print %>% 
  filter(demog_type == "subjectiveses") %>% 
  mutate(
    study = case_when(
    study == "d1" ~ "Experiment 1", 
    study == "d2" ~ "Experiment 2"
    ), 
    task_name = case_when(
      task_name == "CP" ~ "Uniqueness Preference",
      task_name == "RMTS" ~ "Causal RMTS", 
      task_name == "RV" ~ "Raven's Progressive Matrices", 
      task_name == "CD" ~ "Change Detection", 
      task_name == "TD" ~ "Taxonomic-Thematic Similarity" 
    )
  ) %>% 
  rename(
    Study = study, 
    Culture = culture, 
    `Task Name` = task_name, 
    `Beta` = estimate, 
    SE = std.error, 
    t = statistic, 
    p = p.value
  ) %>% 
  ungroup() %>% 
  select(-demog_type) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(p = case_when(
    p == 0.00 ~ " < .001", 
    TRUE ~ as.character(p)
  )) %>% 
  select(Study, Culture, `Task Name`, Beta, SE, t, p) %>% 
  kable(format = "latex", linesep = '') %>% 
  kable_styling(full_width = F, 
                font_size = 9.5)
```

### Maternal Education

Maternal education is often regarded as a proxy for socioeconomic status [@hauser1994measuring; @hoff2005socioeconomic]. In the exploratory analysis, we first treated maternal education as a continuous variable. There was only one significant result: Chinese participants reported having higher maternal education made less situational attribution in the Causal Attribution task. Following common practices in the literature, we also binned the maternal education into a binary variable -- whether participants have received college education or not. The binary variable was not significantly related to any task performance. 

```{r}
demog_print %>% 
  filter(demog_type == "objectiveses") %>% 
  mutate(
    study = case_when(
    study == "d1" ~ "Experiment 1", 
    study == "d2" ~ "Experiment 2"
    ), 
    task_name = case_when(
      task_name == "CA" ~ "Causal Attribution", 
    )
  ) %>% 
  rename(
    Study = study, 
    Culture = culture, 
    `Task Name` = task_name, 
    `Beta` = estimate, 
    SE = std.error, 
    t = statistic, 
    p = p.value
  ) %>% 
  ungroup() %>% 
  select(-demog_type) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  select(Study, Culture, `Task Name`, Beta, SE, t, p) %>% 
  kable(format = "latex", linesep = '') %>% 
  kable_styling(full_width = F, 
                font_size = 9.5,
                latex_options = "HOLD_position")
```


