# Power analysis

We conducted two power analyses: a low assumption t-test power analysis and a high assumption linear mixed effects model power analysis. Under both power analysis frameworks, our sample sizes are well-powered to detect medium and larger effect sizes. 

## Low assumption t-test power analysis

In this framework, we assumed the cultural differences are evaluated with a simple t-test between two samples. We varied the hypothetical effect sizes of the cultural differences. This analysis was conducted using the `pwr` package [@champely2018package]. Under this framework, our sample sizes have more than 80% power to detect effect sizes greater than 0.4 (Cohen’s d).

```{r}
get_power <- function(n, d){
  pwr.t.test(n,d,sig.level=.05)$power
}


sim_d <- merge(
  tibble(
  n = seq(20, 400, 10)
), 
tibble(
  d = seq(0.2, 1.4, 0.1) 
)
) 

sim_d$power <- unlist(pmap(sim_d, get_power))

t_p <- sim_d %>% 
  filter(d < 1.4) %>% 
  ggplot(aes(x = n, y = power, color = as.factor(d), group = d)) + 
  geom_point() + 
  geom_line()+ 
  xlim(10, 350) + 
  ylim(0, 1) + 
  theme_few() + 
  geom_hline(yintercept = 0.8, linetype = 2, color = "gray") + 
  geom_vline(xintercept = 114, linetype = 3, color = "green", alpha = .7) + 
  geom_vline(xintercept = 298, linetype = 3, color = "purple", alpha = .7) + 
  guides(color="none") + 
  labs(title = "Prospective Power Analysis: t-test", 
       color = "Hypothetical Cohen's d") + 
  xlab("Number of Participants (N)") +
  ylab("Power to reject the null at p < .05") + 
  theme(text = element_text(size=6),
          axis.text=element_text(size=10),
          plot.title = element_text(hjust = 0.5, size = 7.2), 
          plot.subtitle = element_text(hjust = 0.5, size = 7.2))
  

```


## High assumption mixed effects linear regression power analysis

Conducting prospective power analysis for mixed-effects linear regression requires more assumptions. Here we specify a simplified model to run the power simulation on. The model predicts a response with culture as the fixed effect, and subjects as the random intercepts. We assumed the fixed effect's intercept and slope as 0.1 and 0.5, respectively. We varied the effect sizes of the model by manipulating different residual standard deviation. We conducted this analysis in the `simr` package [@green2016simr]. Under this framework, our sample sizes have more than 80% power to detect effect sizes greater than 0.6 (Cohen’s d).


```{r eval=FALSE, include=FALSE}
get_sample_size_and_n <- function(fixed_intercept, fixed_slope, df, res, 
                                  rand = list(.5), 
                                  sample_size_range = seq(10, 200, 20)){
  
  fixed <- c(fixed_intercept, fixed_slope)
  model <- makeLmer(y ~ culture + (1|subject), fixef=fixed, VarCorr=rand, sigma=res, data=df)
  
  model_ext <- extend(model, within = "culture" , n = 200)
  
  pcurve <- powerCurve(model_ext, within="culture", breaks = sample_size_range)
  
  pcurve_info <- pcurve$ps
  
  df <- lapply(pcurve_info, 
    function(x){
      return (tibble(
        power = x$x,
        n = x$nrow
      ))
    }
  ) %>% 
    bind_rows() %>% 
    mutate(
      d = fixed_slope / res
    )
  
  return (df)
}

simulation <- lapply(
  # this is to make sure the d we looked at is consistent with the ones in the t-test
  0.5 / seq(0.2, 1.4, 0.1) , 
  function (sigma){
    get_sample_size_and_n(0.1, 0.5, data_df, res = sigma)

  }
) %>% bind_rows()
saveRDS(simulation, here("cached_results/ea/power_analysis.Rds"))

```




```{r}
simulation <- readRDS(here("cached_results/ea/power_analysis.Rds"))

lmer_p <- simulation %>% 
  filter(d < 1.4) %>%
  mutate(d = round(d, 2), 
         power = power / 100) %>% 
  ggplot(aes(x = n , y = power, color = as.factor(d))) + 
  geom_point() + 
  geom_line() + 
  theme_few() + 
  labs(color = "Cohen's d") + 
  geom_hline(yintercept = 0.8, linetype = 2, color = "gray") + 
  geom_vline(xintercept = 114, linetype = 3, color = "green", alpha = .7) + 
  geom_vline(xintercept = 298, linetype = 3, color = "purple", alpha = .7)  + 
  labs(title = "Prospective Power Analysis: mixed effect model", 
       color = "Hypothetical Cohen's d") + 
  xlab("Number of Participants (N)") +
  theme(text = element_text(size=6),
          axis.text=element_text(size=10),
          plot.title = element_text(hjust = 0.5, size = 7.2), 
          plot.subtitle = element_text(hjust = 0.5, size = 7.2), 
         legend.position = "bottom")
  
  #ylab("Power to reject the null at p < .05")
```


```{r fig.height= 7, fig.width=4, fig.cap = "Simulation of power under different sample sizes and effect sizes. The top panel is under t-test assumptions, and the bottom panel is under linear mixed effect model assumptions. X-axis represents the number of particints in each condition. Y-axis represents the estimated power based on the effect sizes and the sample sizes. The horizontal gray dotted line on each plot represents 80\\% power. The two vertical lines, green and purple, represent the minimum sample size (N = 114) and the maximum sample size (N = 293) in our experiments, respectively."}
plot_grid(t_p, lmer_p, nrow = 2, rel_heights = c(1,1.4))
```

