---
title: "exp1_01_main_models"
author: "anjie"
date: "`r Sys.Date()`"
output: html_document
---

Note that since running bayes models are extremely time-intensive, we are not expecting anyone to rerun the code chunk that produced the model. Therefore, I commented out all the code chunks with brms calls. We are going to go directly to the last part of the rmarkdown where we tidy up the model results from the cached model 


If you do with to run the model by yourself, please note: 
- there will be slight numeric difference in the models given the probabilistic nature of the brms 
- you might need to change the file path propertly 



```{r}
library(here)
library(tidyverse)
library(lme4)
library(stringr)
library(lmerTest)
library(rstanarm)
library(bridgesampling)
source(here("processing_pipelines/helper/tidy_model_helper.R"))

d <- read_csv(here("data/03_processed_data/exp1/tidy_main.csv"))
```


```{r}
GLMER_MODEL_DIR <- here("cached_results/exp1/raw_models/glmer_models/")
BAYES_MODEL_DIR <- here("cached_results/exp1/raw_models/bayes_models/")

GLMER_SUMMARY_PATH <- here("cached_results/exp1/glmer_model_summary.RDS")
```


# Run models 

## RMTS

### glmer

```{r}
rmts_df <- d %>% 
  filter(task_name == "RMTS") %>% 
  mutate(choice = case_when(
    resp == "1" ~ 1, # rel
    resp == "0" ~ 0 # obj
         )) %>%
  group_by(subject) %>% 
  mutate(trial_num = row_number()) %>% 
  select(-resp, -task_info, -trial_info, -resp_type)

# model 0: not converging 
#rmts_model <- glmer(choice ~ culture + (trial_num | subject), family = binomial, data = rmts_df)
#unable to evaluate scaled gradientModel failed to converge: degenerate  Hessian with 1 negative eigenvalues

# model 1: 
rmts_model <- glmer(choice ~ culture + (1 | subject), family = binomial, data = rmts_df)

save_model(rmts_model, GLMER_MODEL_DIR)
```

### bayes 

```{r}
full_b_rmts_model <-  brms::brm(
    choice ~ culture + (trial_num | subject), 
    family = "binomial",
    data = rmts_df,
    prior =  c(
              set_prior("normal(0, 0.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0,1.5)", class = "Intercept")),
    save_pars = save_pars(all = TRUE), 
    control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 9000,
    seed = 11111,
    file = here("cached_results/exp1/raw_models/bayes_models/full_b_rmts_model.Rds"))


null_b_rmts_model <-  brms::brm(
    choice ~ 1 + (trial_num | subject), 
    family = "binomial",
    data = rmts_df,
    prior =  c(set_prior("normal(0,1.5)", class = "Intercept")),
    save_pars = save_pars(all = TRUE), 
    control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 9000,
    seed = 11111,
    file = here("cached_results/exp1/raw_models/bayes_models/null_b_rmts_model.Rds"))



```


## Picture free description 

### glmer

```{r}

fd_mention_df <- d %>% 
  filter(task_name == "FD", resp_type == "first_mention_focal") %>% 
    mutate(first_mention = case_when(
    resp == "1" ~ 1, # focal
    resp == "0" ~ 0), # background
    scene = trial_info) %>% 
  select(-resp, -task_info, -resp_type, -trial_info)

fd_mention_model <- glmer(first_mention ~ culture + (1 | subject)+(culture | scene), family = binomial, data = fd_mention_df)

fd_descriptive_df <- d %>% 
  filter(task_name == "FD") %>%
  filter(grepl("imada", resp_type)) %>%
  mutate(description_num = as.numeric(resp),
         scene = trial_info,
         description_type = factor(resp_type)) %>% 
  select(-resp, -task_info, -resp_type, -trial_info)

fd_descriptive_model <- glmer(description_num ~ description_type * culture + (description_type | subject) + (culture | scene), family=poisson, data = fd_descriptive_df)


save_model(fd_mention_model, GLMER_MODEL_DIR)
save_model(fd_descriptive_model, GLMER_MODEL_DIR)

```

### bayes

#### firstmention 

```{r}
full_b_fd_firstmention_model <- brm(
  first_mention ~ culture + (1 | subject)+(culture | scene), 
  data = fd_mention_df, 
  family = "binomial",
  prior =  c(
              set_prior("normal(0, 0.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0,1.5)", class = "Intercept")),
    save_pars = save_pars(all = TRUE), 
    control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    seed = 11111,
    file = here("cached_results/exp1/raw_models/bayes_models/full_b_fd_firstmention_model.Rds")

)

null_b_fd_firstmention_model <- brm(
  first_mention ~ 1 + (1 | subject)+(culture | scene), 
  data = fd_mention_df, 
  family = "binomial",
  prior =  c(set_prior("normal(0,1.5)", class = "Intercept")),
  save_pars = save_pars(all = TRUE), 
  control = list(adapt_delta = 0.999, max_treedepth = 15),
  cores = 4, 
  iter = 5000,
  seed = 11111,
  file = here("cached_results/exp1/raw_models/bayes_models/null_b_fd_firstmention_model.Rds"))
 
```


#### descriptive accounts 


    
```{r}
full_b_fd_descriptives_model <- brms::brm(
   description_num ~ description_type * culture + (description_type | subject) + (culture | scene), 
    data = fd_descriptive_df, 
   family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_fd_descriptives_model.Rds")
)

null_b_fd_descriptives_model <- brms::brm(
   description_num ~ description_type + culture + (description_type | subject) + (culture | scene), 
    data = fd_descriptive_df, 
   family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_fd_descriptives_model.Rds")
)
  
```





## Ebbinghaus 

### glmer

```{r}
ebb_df <- d %>% 
  filter(task_name == "EBB", task_info != "HELPFUL") %>% 
  mutate(correct = case_when(
    resp == "1" ~ 1, #correct
    resp == "0" ~ 0), #incorrect
         context = task_info, 
         size_diff = as.numeric(trial_info), 
         ) %>% 
  select(-resp, -task_info, -trial_info)

#full model
#Model failed to converge with max|grad| = 1.79464 (tol = 0.001, component 1)

#ebb_model <- glmer(correct ~ culture * context * size_diff + (size_diff * context | subject), family = binomial, data = ebb_df, control=glmerControl(optimizer="bobyqa"))
#convergence code 1 from bobyqa: bobyqa -- maximum number of function evaluations exceededModel failed to converge with max|grad| = 0.00144634 (tol = 0.001, component 1)> 


#model 2 (if full does not converge)
ebb_model <- glmer(correct ~ culture * context * size_diff + (context | subject), family = binomial, data = ebb_df, control=glmerControl(optimizer="bobyqa"))
save_model(ebb_model, GLMER_MODEL_DIR)


```

### bayes

```{r}

full_b_ebb_model <-  brms::brm(
   correct ~ culture * context * size_diff + (size_diff * context | subject), 
    data = ebb_df, 
    family = "binomial",
    prior =  c(
              set_prior("normal(0, 0.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0,1.5)", class = "Intercept")),
    save_pars = save_pars(all = TRUE), 
    control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    seed = 11111,
    here("cached_results/exp1/raw_models/bayes_models/full_b_ebb_model.Rds"))

null_b_ebb_model <-  brms::brm(
   correct ~  context * size_diff + (size_diff * context | subject), 
    data = ebb_df, 
    family = "binomial",
    prior =  c(
              set_prior("normal(0,1.5)", class = "Intercept")),
    save_pars = save_pars(all = TRUE), 
    control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    seed = 11111,
    here("cached_results/exp1/raw_models/bayes_models/null_b_ebb_model.Rds"))


```



## Horizon 

### glmer 

```{r}
HZ_height_df <- d %>% 
  filter(task_name == "HZ", resp_type == "hz_height") %>% 
  mutate(
    height = resp
         ) %>% 
  select(-resp, -task_info, -trial_info)


HZ_stkr_area_df <- d %>% 
  filter(task_name == "HZ", resp_type == "stkr_area") %>% 
  mutate(
    stkr_area = (resp/(75*75*3*3)),2) %>% 
#3 from scaling, 75 from conversion: http://auctionrepair.com/pixels.html, 

  select(-resp, -task_info, -trial_info)

hz_stkr_area_model <- lm(stkr_area ~ culture, 
                      data = HZ_stkr_area_df)

hz_height_model <- lm(height ~ culture, 
                      data = HZ_height_df)


hz_stkr_n_df <- d %>% 
  filter(task_name == "HZ", resp_type == "stkr_count") %>% 
  mutate(
    stkr_count = resp
         ) %>% 
  select(-resp, -task_info, -trial_info)

hz_stkr_n_model <- lm(stkr_count ~ culture, 
                      data = hz_stkr_n_df)

save_model(hz_height_model, GLMER_MODEL_DIR)
save_model(hz_stkr_area_model, GLMER_MODEL_DIR)
save_model(hz_stkr_n_model, GLMER_MODEL_DIR)
```

### bayes

#### height 

```{r}
full_b_hz_height_model <-  brms::brm(
    height ~ culture, 
    data = HZ_height_df, 
    family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_hz_height_model.Rds"))

null_b_hz_height_model <-  brms::brm(
    height ~ 1, 
    data = HZ_height_df, 
    family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_hz_height_model.Rds"))
```

#### n

```{r}
full_b_hz_n_model <-  brms::brm(
    stkr_count ~ culture, 
    data = HZ_stkr_n_df, 
    family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_hz_n_model.Rds"))

null_b_hz_n_model <-  brms::brm(
    stkr_count ~ 1, 
    data = HZ_stkr_n_df, 
    family = "gaussian",
   prior =  c(set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_hz_n_model.Rds"))

```


#### area 

```{r}
full_b_hz_area_model <-  brms::brm(
    stkr_area ~ culture, 
    data = HZ_stkr_area_df,
    family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_hz_area_model.Rds"))

null_b_hz_area_model <-  brms::brm(
    stkr_area ~ 1, 
    data = HZ_stkr_area_df,
    family = "gaussian",
   prior =  c(set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_hz_area_model.Rds"))

```



## Symbolict Self Inflation 

### glmer 

```{r}
si_df_r <- d %>% 
  filter(task_name == "SI") %>% 
  filter(resp_type == "inflation_score_ratio") %>% 
  mutate(score = resp) %>% 
  select(-resp, -task_info, -trial_info, -resp_type)


si_df_diff <- d %>% 
  filter(task_name == "SI") %>% 
  filter(resp_type == "inflation_score_diff") %>% 
  mutate(score = resp) %>% 
  select(-resp, -task_info, -trial_info, -resp_type)

ssi_ratio_model <- glm(score ~ culture, family=gaussian, data = si_df_r)
ssi_diff_model <- glm(score ~ culture, family=gaussian, data = si_df_diff)

save_model(ssi_ratio_model, GLMER_MODEL_DIR)
save_model(ssi_diff_model, GLMER_MODEL_DIR)
```


### bayes 

#### ratio 

```{r}

full_b_ssi_ratio_model <-  brms::brm(
    score ~ culture, 
    data = si_df_r, 
    family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_ssi_ratio_model.Rds"))

null_b_ssi_ratio_model <-  brms::brm(
    score ~ 1, 
    data = si_df_r, 
    family = "gaussian",
   prior =  c(set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_ssi_ratio_model.Rds"))

```

#### diff

```{r}

full_b_ssi_diff_model <-  brms::brm(
    score ~ culture, 
    data = si_df_diff, 
    family = "gaussian",
   prior =  c(
              set_prior("normal(0, 2.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_ssi_diff_model.Rds"))

null_b_ssi_diff_model <-  brms::brm(
    score ~ 1, 
    data = si_df_diff, 
    family = "gaussian",
   prior =  c(set_prior("normal(0, 2.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_ssi_diff_model.Rds"))

```



## Unqiue preference 

### glmer

```{r}
up_df <- d %>% 
  filter(task_name == "CP") %>% 
  mutate(choice = case_when(
    resp == "1" ~ 1,       #unique
    resp == "0" ~ 0)  #non-unique
         ) %>% 
  select(-resp, -task_info, -trial_info, -resp_type)

up_model <- glm(choice ~ culture, 
                   family=binomial(link="logit"),
                  data = up_df)

save_model(up_model, GLMER_MODEL_DIR)
```

### bayes

```{r}


full_b_up_model <-  brms::brm(
    choice ~ culture, 
    data = up_df, 
    family = "binomial",
    prior =  c(
              set_prior("normal(0, 0.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0,1.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_up_model.Rds"))

null_b_up_model <-  brms::brm(
    choice ~ 1, 
    data = up_df, 
    family = "binomial",
    prior =  c(set_prior("normal(0,1.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_up_model.Rds"))
```







## Causal Attribution

### glmer

```{r}
ca_df <- d %>% 
  filter(task_name == "CA") %>% 
  mutate(attrib_num = as.numeric(resp),
         attrib_binary = replace(attrib_num, attrib_num > 1, 1),
         trial = trial_info,
         attrib_type = factor(resp_type)) %>% 
  select(-resp, -task_info)

```



```{r}
#ca_model <- glmer(attrib_num ~ attrib_type * culture + (attrib_type | subject) + (culture | trial), family=poisson, data = ca_df, control=glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see ?isSingular

#ca_model_binary <- glmer(attrib_binary ~ attrib_type * culture + (attrib_type | subject) + (culture | trial), family=binomial, data = ca_df, control=glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see ?isSingular

#ca_model1 <- glmer(attrib_num ~ attrib_type * culture + (attrib_type | subject) + (1 | trial), family=poisson, data = ca_df, control=glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see ?isSingular

#ca_model2 <- glmer(attrib_num ~ attrib_type * culture + (1 | subject) + (1 | trial), family=poisson, data = ca_df, control=glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see ?isSingular

#ca_model3 <- glmer(attrib_num ~ attrib_type * culture + (1 | subject), family=poisson, data = ca_df, control=glmerControl(optimizer="bobyqa"))
#boundary (singular) fit: see ?isSingular

ca_model <- glm(attrib_num ~ attrib_type * culture, family=poisson, data = ca_df)

save_model(ca_model, GLMER_MODEL_DIR)
```

### bayes 

```{r}
full_b_ca_model <-  brms::brm(
    attrib_num ~ attrib_type * culture + (attrib_type | subject) + (culture | trial), 
    data = ca_df, 
    family = "poisson",
    prior =  c(set_prior("normal(3, 0.5)", class = "b", coef = "cultureUS")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_ca_model.Rds"))


null_b_ca_model <-  brms::brm(
    attrib_num ~ attrib_type + culture + (attrib_type | subject) + (culture | trial), 
    data = ca_df, 
    family = "poisson",
    prior =  c(set_prior("normal(3, 0.5)", class = "b", coef = "cultureUS")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_ca_model.Rds"))


```



## Ravens

### glmer 

```{r}
rv_df <- d %>% 
  filter(task_name == "RV") %>% 
  mutate(acc = as.numeric(resp)) %>% 
  group_by(subject) %>% 
  mutate(trial = as.factor(row_number())) %>% 
  select(-resp, -task_info, -trial_info, -resp_type)

rv_model <- glmer(acc ~ culture + (1 | subject) + (culture | trial), family = binomial, data = rv_df)

save_model(rv_model, GLMER_MODEL_DIR)
```

### bayes 

```{r}

full_b_rv_model <-  brms::brm(
     acc ~ culture + (1 | subject) + (culture | trial), 
    data = rv_df, 
    family = "binomial",
    prior =  c(
              set_prior("normal(0, 0.5)", class = "b", coef = "cultureUS"),
              set_prior("normal(0,1.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/full_b_rv_model.Rds"))


null_b_rv_model <-  brms::brm(
     acc ~ 1 + (1 | subject) + (culture | trial), 
    data = rv_df, 
    family = "binomial",
    prior =  c(set_prior("normal(0,1.5)", class = "Intercept")),
   control = list(adapt_delta = 0.999, max_treedepth = 15),
    cores = 4, 
    iter = 5000,
    save_pars = save_pars(all = TRUE), 
   file = here("cached_results/exp1/raw_models/bayes_models/null_b_rv_model.Rds"))


```


# tidy up model results 

## glmer 

```{r}
all_models_str <- list.files(GLMER_MODEL_DIR)
all_model_results <- lapply(all_models_str, tidy_model_main) %>% bind_rows()
saveRDS(all_model_results, here("cached_results/exp1/glmer_model_summary.RDS"))
```

## bayes 

```{r}
all_bayes_models_str <- list.files(BAYES_MODEL_DIR, pattern = "*.Rds")

# find pairings 
str_match(all_bayes_models_str[1], "(full|null)_b_\\s*(.*?)\\s*.Rds")


key_words <- unique(sapply(all_bayes_models_str, 
                           function(s){str_match(s,
                                        "(full|null)_b_\\s*(.*?)\\s*.Rds")[,3]}))
                             
# saving each BF calculation because this function crashes R very frequently 
lapply(key_words, function(kw){
  print(kw)
  for (m_name in all_bayes_models_str){
    if (grepl(kw, m_name) & grepl("full", m_name)){
      full_model_name = m_name
      print(full_model_name)
    }
  }
   for (m_name in all_bayes_models_str){
    if (grepl(kw, m_name) & grepl("null", m_name)){
      null_model_name = m_name
      print(null_model_name)
    }
  }
  
  bf <- bayes_factor(bridge_sampler(readRDS(paste0(BAYES_MODEL_DIR, full_model_name))), 
               bridge_sampler(readRDS(paste0(BAYES_MODEL_DIR, null_model_name))))
  print(bf)
  
  saveRDS(bf, file = paste0(here("cached_results/exp1/raw_models/bayes_models/bfs/"), kw, ".rds"))
  
})

## read in all the bayes factor and make a nice summary df 

all_bayes_factor_str <- list.files(paste0(BAYES_MODEL_DIR, "bfs/"), pattern = "*.rds")
bfs_df <- tibble(
  bfs_type = rep(NA_character_, length(all_bayes_factor_str)),
  bf = rep(NA_real_, length(all_bayes_factor_str))
)

for (i in seq(1, length(all_bayes_factor_str), 1)){
  bfs_df$bfs_type[i] <- str_match(all_bayes_factor_str[i], "(.*?)\\s*_model.rds")[,2]
  bfs_df$bf[i] <- readRDS(paste0(BAYES_MODEL_DIR, "bfs/", all_bayes_factor_str[i]))$bf
}

bfs_df <- bfs_df %>% 
  mutate(bf_print = case_when(
    bf < 0.01 ~ "< 0.01",
    bf > 100 ~ "> 100", 
    TRUE ~ paste0("= ", as.character(round(bf,2)))
    ))
    
saveRDS(bfs_df, here("cached_results/exp1/bfs_summary.RDS"))
```

